---
title: "Filtering and summarizing camera data for analysis"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

**Goal**

Filter and summarize data for different analyses.

**Approach**

Filter camera data to remove:

- Videos where no flowers were present
- Videos from afternoon of covering day; these likely reflect behavioral adjustment by hummingbirds, not the experimental outcome or 'normal' visitation

Then, subset this dataset ('full dataset') into different datasets for different analyses.

1. Experimental dataset

**Purpose:** Investigate hummingbird responses to experimental Heliconia removal, following Before-After-Control-Impact design

- Needs cameras to have data from pre AND post periods, because I'm interested in the pre-to-post change
- Only includes data from pre and post periods, not videos reviewed outside of those periods

2. 'Normal' (unmanipulated) dataset

**Purpose:** Understand 'normal' visitation patterns in this study system. Use to tailor resource estimate to different hummingbird groups & understand 'normal' visitation to *Heliconia tortuosa.*

- Not bound by the requirements in #1. 
- Only includes data from control replicates and 'pre' period of treatment replicates; do not want data affected by Heliconia removal

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyr)
library(dplyr)
library(lubridate)
library(ggplot2)
```

## Step 1: Import data
```{r step1, warning=FALSE}
##  Import camera data
## 1. Create column for unique camera ID
## 2. Convert start/end columns into period objects, so can treat them as times when filtering out afternoon videos from covering days
camera_data <- read.csv("../../data/import/Camera_data_with_flower_counts_2016-2018_20220712.csv") %>%
  mutate(camera_id = paste(year, patch, plant_species, camera_num, sep = "_")) %>% 
  mutate(across(c(video_start, video_end), ~lubridate::hm(.))) %>%
  mutate(across(c(sighting_start, sighting_end), ~lubridate::hms(.)))

## Source helper functions
source("../../code/helper_functions/Calculate_basic_summary_stats.R")
source("../../code/helper_functions/Summarize_camera_data.R")
```

## Step 2: Run some initial checks before filtering 
```{r step2, warning=FALSE}
## Check strings that failed to parse in previous step
check01 <- camera_data %>%
  filter(if_any(c(video_start, video_end), ~is.na(.)))

## Are there any missing start/end times for sightings within a video?
## Filter to rows with sighting start/end times (no sightings = NA = no times to parse = warning message)
check02 <- camera_data %>%
  filter(if_any(c(sighting_start, sighting_end), ~is.na(.))) %>%
  filter(sightings_yes_or_no == "Y")

## Are there videos from non-priority dates?
## "Priority" = days in between capture sessions, omitting the day after cover day (for treatment sites) or its equivalent (for control sites)
check03 <- camera_data %>%
  filter(video_priority != 1) %>%
  select(contains("day"), everything()) %>% 
  arrange(exp_day, control_count_day, trmt_day_after_cover)

## Are there videos without any visible flowers?
check06 <- camera_data %>%
  filter(flowers_camera_video == 0)

## It doesn't really make sense to analyze videos with no visible flowers, but out of curiosity...do hummingbirds ever visit anyway?
## "Sighting" = hummingbird appears on camera, "Visit" = hummingbird appears to drink from flower
check04 <- camera_data %>%
  filter(flowers_camera_video == 0 & sightings_yes_or_no == "Y" & visit_type != "none") 

## Are there sightings from the afternoon of cover day? 
## Covering is a big disturbance to the site, so we should NOT use these data...and especially should not consider them 'pre' data!
check05 <- camera_data %>%
  filter(cover_day == 1) %>%
  filter(video_end >= lubridate::hm("11:30")) %>%
  filter(sightings_yes_or_no == "Y")
```

## Step 3: Filter data for all analyses

Remove videos with no flowers on camera (videos were typically not reviewed if they had no flowers, but some were reviewed anyway).
```{r step3a}
## I will still include NAs, since some plants never had flowers visible on video (i.e., MARA-VER, GINGY)
camera_data02 <- camera_data %>%
  filter(flowers_camera_video > 0 | is.na(flowers_camera_video))
```    

Remove sightings from afternoon of cover day (treatment sites only). Here, 'afternoon' = videos starting after 11:30 AM
```{r step3b}
## Videos that start (and end) after 11:30 (will just remove these)
treatment_videos_pm <- camera_data02 %>%
  filter(cover_day == 1 & control_treatment == "treatment") %>%
  filter(video_start > hm("11:30"))

## Videos that span the cutoff time (will change end time to 11:30 and remove sightings after this time)
treatment_videos_am_pm <- camera_data02 %>%
  filter(cover_day == 1 & control_treatment == "treatment") %>%
  filter(video_start < hm("11:30")) %>%
  filter(video_end > hm("11:30"))

## Sightings from afternoon of covering
treatment_sightings_pm <- treatment_videos_am_pm %>%
  filter(sighting_end > hm("11:30"))

## 1. Remove videos from afternoon of cover day (i.e., videos starting after 11:30AM)
## 2. Adjust end time of videos from afternoon of cover day
## 3. Recalculate video length with updated end times
## 4. Make 'adjusted' video length the new video length
camera_data03 <- camera_data02 %>% 
  filter(!(file_id %in% treatment_videos_pm$file_id)) %>% 
  filter(!(sighting_id %in% treatment_sightings_pm$sighting_id)) %>% 
  mutate(video_end_adjust = dplyr::if_else(file_id %in% treatment_videos_am_pm$file_id, hm("11:30"), video_end)) %>%
  mutate(video_length_adjust = as.numeric(video_end_adjust - video_start, "hours")) %>%
  select(row_id:video_length, video_end_adjust, video_length_adjust, everything()) %>%
  select(-video_length) %>%
  rename(video_length = video_length_adjust)
```

Calculate total number of video hours in full dataset (from which smaller datasets are created)
```{r step3c}
hours_per_camera_date <- camera_data03 %>%
  distinct(year, patch, control_treatment, camera_num, date_video, exp_phase, file_id, video_length) %>%
  group_by(year, patch, control_treatment, camera_num, date_video, exp_phase) %>%
  summarise(video_hours = sum(video_length)) %>%
  ungroup()

#Number of hours, summarized across cameras
hours_total <- hours_per_camera_date %>%
  summarise(video_hours = sum(video_hours)) %>%
  ungroup()

hours_total

#How many sightings is this?
camera_data03 %>%
  filter(visit_type != "none") %>%
  distinct(sighting_id) %>%
  filter(!is.na(sighting_id)) %>%
  pull(sighting_id) %>%
  length()
```

## Step 4: Filter data for experimental analyses

Remove videos that do not correspond to 'pre' and 'post' dates

Remove cameras without data pre and post. For the experiment, I'm interested in the pre-to-post change over time. No data from a given time period means that I cannot look at that change!
```{r step4, warning = FALSE, message = FALSE}
#Remove dates that do not correspond to pre and post; sometimes videos were reviewed during setup, for example.
camera_data04 <- camera_data03 %>%
  filter(video_priority == 1)

#Identify cameras that have data from both experimental periods
cameras_pre_and_post <- camera_data04 %>%
  distinct(year, patch, control_treatment, exp_phase, camera_id, date_video) %>%
  group_by(year, patch, control_treatment, exp_phase, camera_id) %>%
  summarise(num_dates = n()) %>%
  ungroup() %>%
  pivot_wider(names_from = exp_phase, values_from = num_dates, values_fill = 0) %>%
  filter(post > 0 & pre > 0)

data_for_experiment <- camera_data04 %>%
  filter(camera_id %in% cameras_pre_and_post$camera_id)

#Calculate hours in this dataset
hours_experiment <- data_for_experiment %>%
  distinct(year, patch, control_treatment, camera_num, date_video, exp_phase, file_id, video_length) %>%
  group_by(year, patch, control_treatment, camera_num, date_video, exp_phase) %>%
  summarise(video_hours = sum(video_length)) %>%
  ungroup() %>%
  summarise(video_hours = sum(video_hours)) %>%
  ungroup()

hours_experiment

#How many sightings is this?
data_for_experiment %>%
  filter(visit_type != "none") %>%
  distinct(sighting_id) %>%
  filter(!is.na(sighting_id)) %>%
  pull(sighting_id) %>%
  length()
```

## Step 5: Filter data for 'normal' visitation

Remove data from 'post' period of treatment replicates (i.e., data affected by experimental *Heliconia* removal)
```{r step5}
data_for_normal_visitation <- camera_data03 %>%
  filter(!(control_treatment == "treatment" & exp_phase == "post"))

#Calculate hours in this dataset
hours_normal_visitation <- data_for_normal_visitation %>%
  distinct(year, patch, control_treatment, camera_num, date_video, exp_phase, file_id, video_length) %>%
  group_by(year, patch, control_treatment, camera_num, date_video, exp_phase) %>%
  summarise(video_hours = sum(video_length)) %>%
  ungroup() %>%
  summarise(video_hours = sum(video_hours)) %>%
  ungroup()

hours_normal_visitation
```

## Step 6: Summarize data for experiment

Calculate visitation rates for each patch-year (across camera IDs, dates)
```{r step6a}
sighting_rates_all_spp = calculate_sighting_rates(data = data_for_experiment, level_org = "plant_species", level_time = "exp_phase", level_bird = "camera_spp_combined", sightings = "with_visit", include_unknown_spp = FALSE) %>%
  mutate(bird_group = "all_spp") #Replace "camera_spp_combined" with "all_spp"

sighting_rates_greh_visa = calculate_sighting_rates(data = data_for_experiment, level_org = "plant_species", level_time = "exp_phase", level_bird = list(greh_visa = c("GREH", "VISA")), sightings = "with_visit", include_unknown_spp = FALSE)

#Combine various summaries
sighting_rates <- sighting_rates_all_spp %>%
  bind_rows(sighting_rates_greh_visa) %>%
  mutate(analysis = ifelse(plant_species == "HETO", "camera_HETO", "camera_non-HETO")) %>%
  select(analysis, bird_group, everything())
```

Calculate visitation rates for each patch-year (across camera IDs, dates) - color-marked birds only

There are some 'marked' birds for 2016, before we marked birds with nail polish, but those are for radio transmitters. I am only interested in birds that can be identified to individual based on color mark, so these data will only reflect the last two years of study (2017-2018)
```{r step6b}
#This summary is at the level of indvidual bird. Since there is species info, will just filter to GREH/VISA
marked_sighting_rates_all_spp = calculate_sighting_rates(data = data_for_experiment, level_org = "plant_species", level_time = "exp_phase", level_bird = "individual_marked", sightings = "with_visit", include_unknown_spp = FALSE) %>%
  mutate(bird_group = "all_spp") #Replace "individual_marked" with "all_spp"

marked_sighting_rates_greh_visa = marked_sighting_rates_all_spp %>%
  filter(bird_species == "GREH" | bird_species == "VISA") %>%
  select(-bird_group) %>%
  mutate(bird_group = "greh_visa")
  
marked_sighting_rates <- marked_sighting_rates_all_spp %>%
  bind_rows(marked_sighting_rates_greh_visa) %>%
  mutate(analysis = ifelse(plant_species == "HETO", "camera_HETO", "camera_non-HETO")) %>%
  select(analysis, bird_group, everything())

#Remove birds not present during pre (at HETO and non-HETO separately)
birds_not_present_during_pre <- marked_sighting_rates %>%
  group_by(analysis, year, patch, exp_phase, color_id) %>%
  summarise(sightings = sum(sightings, na.rm = TRUE)) %>%
  filter(exp_phase == "pre" & sightings == 0) %>%
  mutate(present_during_pre = "no")

marked_sighting_rates <- marked_sighting_rates %>%
  left_join(birds_not_present_during_pre) %>%
  mutate(present_during_pre = ifelse(is.na(present_during_pre), "yes", present_during_pre))
```

Summarize effort for marked birds
```{r}
#How many video hours are there for 2017-2018? Calculate hours in this dataset
hours_experiment_17_18 <- data_for_experiment %>%
  filter(year == "2017" | year == "2018") %>%
  distinct(year, patch, control_treatment, camera_num, date_video, exp_phase, file_id, video_length) %>%
  group_by(year, patch, control_treatment, camera_num, date_video, exp_phase) %>%
  summarise(video_hours = sum(video_length)) %>%
  ungroup() %>%
  summarise(video_hours = sum(video_hours)) %>%
  ungroup()

hours_experiment_17_18

#How many marked individuals were detected on camera?
marked_individuals_on_camera <- marked_sighting_rates %>%
  distinct(year, patch, bird_species, color_id)

(num_marked_individuals_on_camera <- marked_individuals_on_camera$color_id %>% length())

#How does this number compare to the number of individuals that were color marked? I.e., what proportion of color-marked birds were detected on camera?
captures <- read.csv("../../data/import/Hummingbird_captures_2010-2018_20220713.csv") %>%
  select(control_treatment, exp_phase, year, patch = site, everything())

captures_marked_birds <- captures %>%
  filter(!is.na(control_treatment)) %>%
  filter(exp_phase == "capture_1") %>%
  filter(status != "DR") %>%
  filter(!is.na(colors)) %>%
  unite(color_id, year, patch, species, colors, sep = "_", remove = FALSE)

(num_marked_indivduals <-unique(captures_marked_birds$color_id) %>% length())

duplicated_marks <- captures_marked_birds %>%
  filter(duplicated(color_id)) %>%
  select(year, patch, species, sex, color_id)

#According to capture data, 142 birds were marked with nail polish during initial capture (2017-2018 only). 140 were unique to year, patch, and species.
#Duplicated marks: 
#2017_201_VISA_Y (same color, but on different sexes, so would have been distinguishable. But not seen on camera)
#2018_29_STRH_B (seen on camera, sex not distinguishable)
#Note: if calculate number of marked birds according to 'color_marks' datasheets, 143 birds were marked with nail polish during initial capture (2017-2018 only), because this includes CHHU from p200 establishment

#Percentage of color-marked birds detected on camera
num_marked_individuals_on_camera/num_marked_indivduals
```

## Step 7: Explore data related to *Heliconia*, using 'normal' visitation data

What species visit Heliconia?
```{r step7a}
#To level of species
heto_sightings_by_species <- calculate_sighting_rates(data = data_for_normal_visitation, level_org = "plant_species_across_sites", level_time = "all", level_bird = "camera_spp_separate", sightings = "with_visit", include_unknown_spp = TRUE) %>% 
  filter(plant_species == "HETO") %>%
  filter(sightings > 0) %>%
  mutate(bird_sex = "all")

#Before summarizing to level of sex, combine unknown sex categories, i.e. convert unknown male (UM) and unknown female (UF) to unknown
data_for_heto_sightings_by_sex <- data_for_normal_visitation %>%
    mutate(bird_sex = ifelse(bird_sex == "UM" | bird_sex == "UF", "U", as.character(bird_sex)))
  
heto_sightings_by_sex <- calculate_sighting_rates(data = data_for_heto_sightings_by_sex, level_org = "plant_species_across_sites", level_time = "all", level_bird = "camera_spp_separate_sex", sightings = "with_visit", include_unknown_spp = TRUE) %>% 
  filter(plant_species == "HETO") 

#Combine for Supp material
heto_sightings <- heto_sightings_by_species %>%
  bind_rows(heto_sightings_by_sex) %>%
  arrange(bird_species, desc(sightings))

#How many video hours for this dataset?
hours_normal_visitation_heto <- data_for_normal_visitation %>%
  filter(plant_species == "HETO") %>%
  distinct(year, patch, control_treatment, camera_num, date_video, exp_phase, file_id, video_length) %>%
  group_by(year, patch, control_treatment, camera_num, date_video, exp_phase) %>%
  summarise(video_hours = sum(video_length)) %>%
  ungroup() %>%
  summarise(video_hours = sum(video_hours)) %>%
  ungroup()

hours_normal_visitation_heto
```

How many hummingbird sightings per *Heliconia* plant (inflorescence) per day?
```{r step7b}
#Summarize using 'normal' data, by camera number. Each camera was positioned at a single Heliconia inflorescence
heto_sightings_per_date <- calculate_sighting_rates(data = data_for_normal_visitation, level_org = "camera_num", level_time = "date_video", level_bird = "camera_spp_combined", sightings = "with_visit", include_unknown_spp = TRUE) %>% 
  filter(plant_species == "HETO")

heto_sightings_per_date_sum <- heto_sightings_per_date %>%
  calculate_basic_summary_stats(variable = sightings)

heto_sightings_per_date_sum

#Sightings per date is the most meaningful metric...but not all dates have 12 hours of video. Can I extrapolate from sightings/hour? Only problem would be if rate isn't constant throughout day
heto_sightings_per_12_hours <- heto_sightings_per_date %>%
  mutate(sightings_per_12hours = sightings_per_hour * 12) %>% #Hourly sighting rate multiplied by 12
  select(-sightings_per_hour)

heto_sightings_per_12_hours_sum <- heto_sightings_per_12_hours %>%
  calculate_basic_summary_stats(variable = sightings_per_12hours)

heto_sightings_per_12_hours_sum #Slightly higher values when multiply by 12
```

## Step 8: Export
```{r step8}
## Camera data, filtered but not summarized
write.csv(data_for_experiment, "../../data/export/intermediate/Camera_data_filtered_for_experiment.csv") 
write.csv(data_for_normal_visitation, "../../data/export/intermediate/Camera_data_filtered_for_normal_visitation.csv") 

## Summarized data for analysis of experiment
write.csv(sighting_rates, "../../data/export/for_analysis/Camera_visitation_rates.csv") 
write.csv(marked_sighting_rates, "../../data/export/for_analysis/Camera_visitation_rates_marked_birds.csv")

##  Summarized data of Heliconia visitation
write.csv(heto_sightings, "../../data/export/supp_tables/Heliconia_visitor_summary.csv")
```
