---
title: "Calculating capture & recapture rates"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

**Overall goal**

Calculate two response variables:

1. Capture rates: number of hummingbirds caught per net-hour

- Will keep these columns separate so can model rate with an offset using GLMM

2. Recapture rates: proportion of birds captured (and tagged) during the 'pre' period that were recaptured during the 'post' period

- Will keep these columns separate so can model rate as counted proportion using GLMM

**Additional goals**

Explore capture data and summarize for results/methods. How many total hummingbirds captured? Recaptures? etc.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
```

## Step 1: Import data and functions

```{r step1}
#Capture data. This is all capture data, spanning all years of the project.
#1. Subset just to data for the experiment (2016-2018)
#2. Remove data from establishment period (initial failed capture in p200)
#3. Remove day recaptures
#4. Remove bird that died during first capture (not around to be recaptured in post)
#5. Add column for bird ID, because birds were sometimes not banded. Using colors instead in those cases. This ID will allow me to identify recaps between pre/post a given patch/year
captures <- read.csv("../../data/import/data/captures/Hummingbird_captures_2010-2018.csv") %>%
  rename(patch = site) %>%
  filter(year >= 2016) %>%
  filter(exp_phase == "capture_1" | exp_phase == "capture_2") %>% 
  filter(status != "DR") %>%
  filter(!(grepl("died", notes))) %>%
  mutate(bird_id = ifelse(is.na(band_number), paste(year, patch, bird_species, colors, sep = "_"), paste(year, patch, bird_species, band_number, sep = "_"))) %>%
  mutate(date = lubridate::ymd(date)) %>%
  mutate(across(c(year, patch), as.character)) %>% 
  mutate(trap_id = as.integer(trap_id))

#Capture effort (net-hours)
net_hours <- read.csv("../../data/export/intermediate/Net-hours_2016-2018.csv") %>%
  mutate(net_hours = round(net_hours_adjusted, digits = 4)) %>%
  mutate(date = lubridate::ymd(date)) %>%
  mutate(across(c(year, patch), as.character))

#Scientific names
bird_species_names <- read.csv("../../data/import/data/Hummingbird_codes_species_list.csv")

#Functions
source("../../code/helper_functions/Calculate_basic_summary_stats.R")
```

## Step 2: Explore capture data (totals)

Calculate the following for the results/Supp material.

- Total number of captures, omitting day recaptures
- Total number of individuals captured

First, double check to make sure day recaptures have been removed. I filtered them out above (status != "DR"), but it's possible some could have slipped through.
```{r step2a}
recaps_within_day <- captures %>%
  distinct(patch, date, bird_species, band_number) %>%
  filter(!is.na(band_number)) %>% #NA for birds not banded
  group_by(date, bird_species, band_number) %>%
  summarise(num_captures = n()) %>%
  filter(num_captures > 1)

#Yes, they have all been removed.
```

Total of number of captures and individuals
```{r step2b}
#Total number of captures (omitting day recaptures)
total_captures <- captures %>%
  summarise(total_birds = n())

total_captures

#Total captures by species
total_captures_per_species <- captures %>%
  group_by(bird_species) %>%
  summarise(num_captures = n()) %>%
  arrange(desc(num_captures))

total_captures_per_species

#Total number of individuals captured and banded
banded_individuals <- captures %>%
  distinct(bird_species, band_number) %>%
  filter(!is.na(band_number))

num_banded_individuals <- banded_individuals$band_number %>% length() + 2

#318 birds banded + 2 birds that were probably band typos (see below) --> 320 birds banded

#Total number of individuals captured and not banded
unbanded_individuals <- captures %>%
  filter(is.na(band_number) | band_number == "NA")

num_unbanded_individuals <- unbanded_individuals$band_number %>% length()

#Total individuals captured
(total_captured_individuals = num_banded_individuals + num_unbanded_individuals)

#320 BANDED + 12 UNBANDED = 332
```

## Step 3: Identify and summarize recaptures on different levels

- Between sites (across years)
- Within sites (across years)
- Within sites (within year, i.e. during experiment)

Birds recaptured in different sites
```{r step3a}
#Calculate number of sites/bird to get recaptures across sites
recaps_across_sites <- captures %>%
  distinct(patch, bird_species, band_number) %>%
  filter(!is.na(band_number)) %>% #NA for birds not banded
  group_by(bird_species, band_number) %>%
  summarise(num_sites = n()) %>%
  arrange(desc(num_sites)) %>%
  filter(num_sites > 1)

#There are supposedly four birds caught in different patches, but only half of these seem probable.

#Possible recaptures across sites: 
#GCBR SA3779 - transmitter frequency 131. Caught 3 times in 2017! Banded in p24, caught in pre and post, and then caught ~ 1 mo later in p203
#GCBR SA4102 - banded in p203 in 2017, caught in 2018 in p24
#Interestingly, both of these are GCBR going between p24 and p203, which are only ~600m apart.

#Unlikely recaptures across sites
#RTAH SA4722 - both captures in 2017, p204/p49. Confirmed data entry error for initial capture - new band, NOT a recapture. Missing datashet for supposed (new) capture on 29-Apr-17 but probably a typo in that band number.
#STRH SA4207 - both captures in 2018, p29/p10. Suspected typo - new band in both, NOT a recapture.

#Either way, birds moving between sites seems pretty rare
length(recaps_across_sites$band_number)/total_captured_individuals
```

Birds recaptured across years
```{r step3b}
recaps_across_years <- captures %>%
  distinct(year, bird_species, band_number) %>% #Don't bother with color marks; will have worn off.
  filter(!is.na(band_number)) %>% #NA for birds not banded
  group_by(bird_species, band_number) %>%
  summarise(num_years = n()) %>%
  filter(num_years > 1)

length(recaps_across_years$band_number)

#15 birds caught in different years. This includes 1 bird (GCBR SA4102) recaptured across sites
#Interestingly, the only birds caught in all three years were in p10: GREH SA4005 and STRH SA4200
```

Birds recaptured within an experiment (i.e., birds caught pre and post); this is what I'm interested in
```{r step3c}
recaps_within_experiment <-  captures %>%
  distinct(year, patch, exp_phase, bird_species, bird_id, band_number, colors) %>% #Not all birds banded, so use colors marks as well.
  group_by(year, patch, bird_species, bird_id, band_number, colors) %>%
  summarise(num_captures = n()) %>%
  filter(num_captures > 1)

length(recaps_within_experiment$bird_id)

#34 birds caught in both pre and post. Will use this later on to calculate recapture rate (proportion of birds tagged pre that were re-captured post)
```

~The Math~

The breakdown in the difference between 383 total captures and 332 unique individuals (i.e., how the 51 recaptures are partitioned)

- 2 bird recaptured across sites --> +2
- 15 birds recaptured across years, but 1 of those birds already accounted for in birds recaptured across sites (-1). But then two birds were re-caught 3 times, not 2 (+2) --> +16
- 34 birds recaptured within experiment, but 1 of those birds already accounted for in birds recaptured across years (STRH SA4200) --> +33

2 + 16 + 34 = 51 recaps

## Step 4: Make a summary table of bird species detected per site
```{r step4}
#Captures of unique individuals per site, by species
species_per_site <- captures %>%
  distinct(patch, bird_species, band_number) %>%
  group_by(patch, bird_species) %>%
  summarise(num_birds = n()) %>%
  left_join(bird_species_names)

#Convert to wide form, with just an 'x' if species was detected in the site
species_per_site_x <- species_per_site %>%
  mutate(detected = "x") %>%
  select(-num_birds) %>%
  pivot_wider(names_from = patch, values_from = detected, values_fill = "")

#Individuals per species
individuals_per_species <- species_per_site %>%
  group_by(bird_species) %>%
  summarise(num_birds = sum(num_birds))

#Individuals per species - OMITTING BIRDS FROM 'POST' PERIOD IN TREATMENT (i.e., for description of relative abundance/what is 'normal' for study system)
individuals_per_species_normal <- captures %>% 
  filter(!(control_treatment == "treatment" & exp_phase == "capture_2")) %>%
  distinct(patch, bird_species, band_number) %>%
  group_by(bird_species) %>%
  summarise(num_birds_normal = n())

#Combine data. This is a combined summary of (a) bird species included in capture data, and (b) which sites had which birds
capture_summary_table <- species_per_site_x %>%
  left_join(individuals_per_species) %>%
  left_join(individuals_per_species_normal) %>%
  left_join(total_captures_per_species) %>%
  mutate_at(vars(num_birds_normal), ~ifelse(is.na(.), 0, .)) %>%
  arrange(desc(num_birds))
```

## Step 5: Summarize capture data for analysis

I want to summarize capture numbers for:

- All species combined ('all_spp')
- *Heliconia* specialists, green hermits and violet sabrewings ('greh_visa')

```{r step5}
#All species combined
num_birds_all_species  <- captures %>% 
  group_by(year, patch, control_treatment, date, exp_phase) %>% 
  summarise(num_birds = n()) %>% 
  ungroup() %>% 
  right_join(net_hours) %>% #Add info about net hours. Right join so can fill in missing data with zeroes
  mutate(num_birds = ifelse(is.na(num_birds), 0, num_birds)) %>%  #Some patches had no captures (of any species) - making these zero
  mutate(bird_group = "all_spp")

#GREH/VISA only
num_birds_greh_visa <- captures %>% 
  filter(bird_species == "GREH" | bird_species == "VISA") %>% 
  group_by(year, patch, control_treatment, date, exp_phase) %>% 
  summarise(num_birds = n()) %>% 
  ungroup() %>% 
  right_join(net_hours) %>% #Add info about net hours. Right join so can fill in missing data with zeroes
  mutate(num_birds = ifelse(is.na(num_birds), 0, num_birds)) %>%  #Some patches had no captures (of any species) - making these zero
  mutate(bird_group = "greh_visa")

#Combine, calculate capture rates
capture_rates <- num_birds_all_species %>%
  bind_rows(num_birds_greh_visa) %>%
  select(bird_group, year, patch, control_treatment, date, exp_phase, net_hours = net_hours_adjusted, num_birds) %>%
  arrange(bird_group, year, patch, control_treatment, exp_phase) %>%
  mutate(capture_rate = num_birds/net_hours,
         capture_rate = round(capture_rate, digits = 4))
```

*Notes*

There was 1 instance where no birds (of any species) were captured during pre period
- 2017 p137 (control) --> also no birds during post period

There were 3 *additional* instances where no GREH or VISA were captured during pre period
- 2016 p200 (control)
- 2017 p200 (treatment)
- 2018 p137 (control) --> also no GREH/VISA during post period

Need to decide whether or not to include replicates that didn't have any captures during 'pre' period. Including would be biased *against* finding a treatment effect (decline in capture numbers), since you can only go up from zero.

DECISION: For space use variables (captures + telemetry), remove replicates without confirmed presence of hummingbird(s) in focal area during 'pre' period. This also makes since because if bird was not using site during pre period, we wouldn't expect them to register our treatment.
```{r}
no_birds_in_pre_replicates <- capture_rates %>%
  filter(exp_phase == "capture_1" & num_birds == 0) %>%
  mutate(year_patch_bird_group = paste(year, patch, bird_group, sep = "_"))

no_birds_in_pre_replicates

#This is a consistent problem in p137 and p200 (across years)

capture_rates_birds_in_pre_only <- capture_rates %>%
  mutate(year_patch_bird_group = paste(year, patch, bird_group, sep = "_")) %>%
  filter(!(year_patch_bird_group %in% no_birds_in_pre_replicates$year_patch_bird_group))
```

## Step 6: Summarize recapture data for analysis

Here, 'recaptures' = birds caught during both of the capture sessions, pre AND post

Recapture rate = proportion of birds tagged in first capture that were caught during second capture

Filter data to be used in recapture analysis
```{r step6a}
#1. Remove birds without any identifying marks. Cannot ensure independence between measurements if not marked.
#2. Remove birds with suspect band numbers (likely typos in band number are indicated by asterisk as of 1/25/2021). Need to remove these birds from recapture analysis, because recaptures based on band number match
data_for_recaptures <- captures %>%
  filter(!(grepl("*", band_number, fixed = TRUE))) %>%
  select(bird_id, everything())
```

Identify recaptures
```{r step6b}
#Birds that were captured during pre period
pre_birds <- data_for_recaptures %>%
  filter(exp_phase == "capture_1")

#Birds that were captured during post period
post_birds <- data_for_recaptures %>%
  filter(exp_phase == "capture_2")

#Identifying pre-post recaps (for a given patch, post %in% pre)
#THIS IS THE SAME AS 'recaps_within_experiment', above
recaptures <- post_birds %>%
  filter(bird_id %in% pre_birds$bird_id) %>% 
  select(year, patch, control_treatment, bird_id, bird_species)

#What percentage of birds captured during pre were recaptured during post?
(num_pre_birds <- pre_birds$band_number %>% length())
(num_recaptures <- recaptures$bird_id %>% length())

num_recaptures/num_pre_birds
```

*Of 203 birds [without suspected band typos] captured during the 'pre' period, 34 were captured during the post (~17% overall recapture rate)*

Add column (0/1) to dataset of birds captured during pre, indicating whether they were they recaptured during post. This is for if I want to incorporate individual covariates that might determine whether a bird was recaptured later on.
```{r step6c}
pre_birds_with_recap_status <- pre_birds %>%
  mutate(recaptured_post = ifelse(bird_id %in% recaptures$bird_id, 1, 0)) %>%
  select(bird_id, recaptured_post, everything())
```

Now, summarize # of birds re-captured for:

- All species combined ('all_spp')
- *Heliconia* specialists, green hermits and violet sabrewings ('greh_visa')

```{r step6d}
#All species
num_recaptures_all_species  <- recaptures %>% 
  group_by(year, patch, control_treatment) %>% 
  summarise(num_birds = n()) %>% 
  ungroup() %>%
  mutate(bird_group = "all_spp")

#GREH/VISA only
num_recaptures_greh_visa <- recaptures %>% 
  filter(bird_species == "GREH" | bird_species == "VISA") %>% 
  group_by(year, patch, control_treatment) %>% 
  summarise(num_birds = n()) %>% 
  ungroup() %>%
  mutate(bird_group = "greh_visa")

#Combine data
num_recaptures <- num_recaptures_all_species %>%
  bind_rows(num_recaptures_greh_visa) %>%
  rename(num_recaps_post = num_birds)
  
recapture_rates <- capture_rates %>%
  select(bird_group, year, patch, control_treatment, exp_phase, num_birds) %>%
  pivot_wider(names_from = exp_phase, values_from = num_birds) %>%
  rename(num_birds_pre = capture_1, num_birds_post = capture_2) %>%
  left_join(num_recaptures) %>%
  mutate(num_recaps_post = ifelse(is.na(num_recaps_post), 0, num_recaps_post)) %>% #Fill in zeroes for no recaps
  mutate(recap_rate = num_recaps_post / num_birds_pre) #Will be NaN if denominator is zero (no birds caught during pre)
```

## Step 7: Export data

```{r step7}
#CAPTURES
#For main analysis
write.csv(capture_rates_birds_in_pre_only, "../../data/export/for_analysis/Capture_rates.csv", row.names = FALSE)

#For Supp table
write.csv(capture_summary_table, "../../data/export/supp_tables/extra/Captured_species_per_site_summary_table.csv", row.names = FALSE)

#RECAPTURES
#For main analysis
write.csv(recapture_rates, "../../data/export/for_analysis/Recapture_rates.csv", row.names = FALSE)

#For analysis of pre-post changes in body condition
write.csv(recaptures, "../../data/export/intermediate/Birds_recaptured_post.csv", row.names = FALSE)

#For potential future analysis of whether individual attributes influence recapture (0/1 for each bird)
write.csv(pre_birds_with_recap_status, "../../data/export/intermediate/Birds_captured_pre_with_recap_status.csv", row.names = FALSE) 
```
