---
title: "Filtering data for relative body mass analysis"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

**Goal**

Prepare capture data for analysis of relative body mass. Analytical plan is outlined below but conducted in a separate scripts.

**Approach**

Analyze hummingbird body mass relative to mass predicted for a given wing length (within a species).

1. Using data from all years of hummingbird captures (2018-2018), create allometric equations for each species: log(mass) ~ log(wing length)

2. For each recaptured hummingbird from the experiment (2016-2018), use the allometric equation to calculate predicted body mass for a given wing length. For each bird, I therefore need data about wing length and body mass.

3. Calculate relative mass as measured body mass divided by predicted body mass. Birds with values <1 are lighter than expected for their structural size; similarly, birds with values >1 are heavier than expected for their structural.

4. Analyze how Heliconia removal influences change in relative body mass.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(purrr)
library(glmmTMB)
library(emmeans)
```

## Step 1: Get data
```{r}
#Hummingbirds species names
bird_names <- read.csv("../../data/import/data/Hummingbird_codes_species_list.csv") %>%
  select(bird_species, bird_scientific_name, bird_common_name)

#Capture data (2010-2018)
#Add color_id column because sometimes birds were not banded. Using colors instead in those cases. This ID will allow me to identify recaps between pre/post a given patch/year
#Remove measurements before bird was fed sugar water, since that could lead to short-term increase the body mass
#Remove day recaptures (hummingbirds captured twice during same capture session)
captures_all_years <- read.csv("../../data/import/data/captures/Hummingbird_captures_2010-2018.csv") %>%
  left_join(bird_names) %>%
  rename(patch = site) %>%
  mutate(patch = ifelse(patch == "33-Jardin", 33, patch)) %>%
  mutate(bird_id = ifelse(is.na(band_number), paste(year, patch, bird_species, colors, sep = "_"), paste(year, patch, bird_species, band_number, sep = "_"))) %>% 
  select(bird_id, everything()) %>%
  filter(!grepl("comio antes de pesar|fed before weight|fed b/f", notes, ignore.case = TRUE)) %>%
  filter(status != "DR") %>%
  select(year, patch, control_treatment, exp_phase, bird_species, bird_sex = sex, mass, wing_length, bird_id, bird_scientific_name, bird_common_name)

#Hummingbirds captured pre AND post during Heliconia removal experiment (2016-2018)
recap_list <- read.csv("../../data/export/intermediate/Birds_recaptured_post.csv")
```

## Step 2: Prepare recapture data (experiment only) for further analysis

Subset capture data to hummingbirds recaptured during Heliconia removal experiment (2016-2018)
```{r}
recaptures_experiment <- captures_all_years %>%
  filter(bird_id %in% recap_list$bird_id)
```

To calculate a relative body mass, I need wing length (the measure of structural size) and the measured body mass. Make sure recaptured birds have morphometric measurements.
```{r}
#However, sometimes a recaptured bird had multiple wing measurements. Will average across these measurements.
average_wing_lengths <- recaptures_experiment %>%
  group_by(bird_id) %>%
  summarise(wing_length = mean(wing_length, na.rm = TRUE)) %>%
  ungroup()

#Remove original wing lengths, replace with average lengths
#Remove any birds without any wing measurements; e.g., some birds didn't have wing length measurements pre or post (p29, bc we got very busy at banding table)
recaptures_experiment_measurements <- recaptures_experiment %>%
  select(-wing_length) %>%
  left_join(average_wing_lengths) %>%
  arrange(bird_id) %>%
  filter(!is.na(wing_length)) %>%
  filter(!is.na(mass))
```

Remove birds without body mass measurements per and post. I'm interested in the pre-to-post change, so need measurements in both periods.
```{r}
birds_missing_periods <- recaptures_experiment_measurements %>%
  group_by(bird_id) %>%
  summarise(num_periods = n()) %>%
  ungroup() %>%
  filter(num_periods < 2)

#Remove birds without pre and post measurements
recaptures_experiment_for_analysis <- recaptures_experiment_measurements %>%
  filter(!(bird_id %in% birds_missing_periods$bird_id)) 

#How many individuals is this final dataset?
#All species
unique(recaptures_experiment_for_analysis$bird_id) %>% length()

#GREH/VISA
recaptures_experiment_for_analysis %>%
  filter(bird_species == "GREH" | bird_species == "VISA") %>%
  distinct(bird_id) %>%
  pull(bird_id) %>%
  length()
```

## Step 3: Prepare capture data (all years) for further analysis (i.e., allometric equations)
```{r}
#Remove original data for recaptures and replace with average wing lengths
#Remove data for bird species that are not in recapture dataset. I only need allometric equations for recaptured species
#Add column indicating whether bird is a recapture bird from experiment
recaptures_bird_species <- recaptures_experiment_for_analysis %>%
  distinct(bird_species)

mass_wing_data_for_analysis <- captures_all_years %>%
  filter(!(bird_id %in% recaptures_experiment_measurements$bird_id)) %>% #Remove original data associated with recaptures (i.e., bird caught in pre and post)
  bind_rows(recaptures_experiment_measurements) %>% #Add in averaged measurements
  filter(!is.na(wing_length)) %>%
  filter(!is.na(mass)) %>%
  filter(bird_species %in% recaptures_bird_species$bird_species) %>%
  mutate(experiment_bird = ifelse(bird_id %in% recaptures_experiment_for_analysis$bird_id, "yes", "no"))
```

## Step 4: Export data
```{r}
#This dataset has all the data I need for analysis; recaptured individuals can be identified by the 'experiment_bird" column
write.csv(mass_wing_data_for_analysis, "../../data/export/for_analysis/Capture_morphological_measurements.csv", row.names = FALSE)
```