---
title: "Processing and summarizing pollen tube data"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

**Context and goals**

These are the data for pollination success; I determined whether or not flowers were pollinated based on the presence of pollen tubes in the style. This was done by examining the style under a microscope. While looking for pollen tubes, the observer did not know what site or time period the styles came from; they just knew the species.

Here, I:

- Add in the data about which site/date the styles (flowers) came from. This was recorded on the vial that held the styles, before lab work began.

- Explore the data and determine which plant species had enough pollen tubes for analysis (pollen tubes were pretty rare overall)

- Summarize data to create my response variable: proportion of flowers that were pollinated.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(dplyr)
library(tidyr)
library(ggplot2)
```

## Step 1: Import data and functions
```{r step1}
#Data about style, from what was written on vial
vials <- read.csv("../../data/import/Vial_info_for_pollen_tubes_2016-2018.csv") %>%
  select(-X)

#Data about which dates were 'pre' vs. 'post
exp_info <- read.csv("../../data/import/Experiment_dates_2016-2018.csv")

#Data from microscope work (counts of # pollen tubes per style). Initially entered on Google Drive
tubes <- read.csv("../../data/import/Pollen_tube_microscope_work_from_GD_20210831.csv")
```

## Step 2: Add experiment info (pre/post, control/treatment) to vial info based on date *before* styles were collected

The date written on the vial was the date that styles were *collected*. This is *not* necessarily the date the flowers were open/could be pollinated. Here, I assume that was the day before styles were collected, which is a reasonable assumption for plant species with single-day flowers (such as *Heliconia*).

```{r step2}
#Prepare data for join
exp_info_to_join <- exp_info %>%
  mutate_all(as.character) %>%
  mutate(date_flowered = lubridate::mdy(date)) %>% #Rename to match vial info below
  select(year, patch, date_flowered, exp_phase, control_treatment = control_trmt, exp_day, cover_day = trmt_cover_day, day_after_cover_day = trmt_day_after_cover)

#1. Calculate the dates 1 day before the date written on vial
#2. Join to experiment info
#3. Some vials had no date, but have experimental period (pre/post) written on the vial. Assign them a period (phase) based on what is written on vial ('exp_phase_vial')
vials_exp_info <- vials %>%
  mutate_all(as.character) %>%
  mutate(date_collected = lubridate::ymd(date_collected)) %>%
  mutate(date_flowered = date_collected - 1 ) %>%
  left_join(exp_info_to_join) %>%
  mutate(exp_phase = ifelse((exp_phase_vial != "" & !is.na(exp_phase_vial)), exp_phase_vial, exp_phase)) %>%
  select(entered_by:patch, control_treatment, starts_with("plant_species"), starts_with("focal_nf"), starts_with("date"), starts_with("exp_phase"), exp_day, cover_day, day_after_cover_day, everything()) %>%
  arrange(as.numeric(box_number), as.numeric(vial_number)) %>%
  rename(vial_notes = notes)

#Check: does each vial from experiment have experiment info?
check01 <- vials_exp_info %>%
  filter(is.na(exp_phase)) %>% #These are rows with issues (need the date to get any info about exp_phase)
  filter(patch != "" & !is.na(patch)) %>% #Remove vials without patch numbers
  filter(year == "2016" | year == "2017" | year == "2018") %>% #Remove vials from non-experimental years (these are definitely long-term, patch-level pollen tubes)
  filter(patch %in% exp_info$patch) %>% #Remove vials with patch numbers not in Heliconia removal experiment info (these are long-term, patch-level pollen tubes)
  arrange(date_flowered, year, patch)

#Technically no; the styles collected on setup day do not have any experiment info. This occurs because the *before* setup is not considered part of the experiment.
```

## Step 3: Combine pollen tube data (microscope work) with vial + experiment info
```{r step3}
#1. Distinguish between the date vial data were entered and the date of microscope work
#2. Separate vial ID from slide label (which can include subsample ID and slide number)
#3. Sort out subsample_ID vs. slide_number. If there was no subsample (no A, B, etc.), the data in the 'subsample' column is actually the slide 
#4. If subsample_ID is a number (instead of a letter), assign that value to the slide_number
#5. If subsample_ID is a number (instead of a letter), make it NA
#6. If slide number is still NA (i.e. was never assigned) it is automatically a '1'
tubes_to_join <- tubes %>%
  rename(date_reviewed = date, review_notes = notes) %>% 
  separate(col = slide_label, into = c("vial_ID", "subsample_ID", "slide_number"), remove = FALSE) %>%
  mutate(slide_number = ifelse(!is.na(as.numeric(subsample_ID)), subsample_ID, slide_number)) %>%  
  mutate(subsample_ID = ifelse(!is.na(as.numeric(subsample_ID)), NA, subsample_ID)) %>% 
  mutate(slide_number = ifelse(is.na(slide_number), 1, slide_number)) %>%
  mutate(row_id = 1:length(vial_ID)) %>%
  select(row_id, everything())
  
#Join...
tubes_vials_exp_info <- tubes_to_join %>%
  left_join(vials_exp_info) %>%
  mutate(exp_phase = factor(exp_phase, ordered = TRUE, levels = c("pre","post"))) %>%
  mutate(across(c('tubes_total_min', 'tubes_total_max', 'tubes_base_min', 'tubes_base_max'), ~as.numeric(.))) %>%
  mutate(tube_presence = ifelse(tubes_total_min > 0, 1, 0)) %>%
  mutate(tube_presence = ifelse(is.na(tubes_total_min) | tubes_total_min == "NA", NA, tube_presence)) %>% #If count is NA, tube is not present
  mutate(tube_presence = factor(tube_presence)) %>%
  select(row_id:style_number, starts_with("tube"), everything(), -starts_with("X"))
```

## Step 4: Identify styles that should be included in analysis

Not all dates and plants should be analyzed. 

These data should be **included**:

- Numbered experimental days (i.e. days assigned pre/post), which are the days between the capture 1 and capture 2. These days also correspond to when we have telemetry and camera data.

- 'Focal' plants (plants at stations)
  
- Plants with styles (vials) from pre *and* post periods, because I'm interested in the pre-to-post change

These data should be **excluded**:

- Cover day in treatment sites
  
- Day after covering in treatment sites ('adjustment day')
  
- Instances were flowers collected in the 'post' period were known to be open during the 'pre' period (i.e., blurred delineation between experimental periods)
  
- 'Non-focal' plants; these styles were collected haphazardly from around the focal area, and are probably especially noisy. Also, I cannot be sure if same plant was sampled pre and post.

```{r step4a}
#Note: initially I ran these filtering steps on just the vial/experiment info to identify 'priority' vs. 'non-priority' vials for microscope work. But now that the lab work is done, I'm filtering the actual data. For instance, I ended up analyzing quite a few 'test' (non-priority) styles while ironing out methods, and these are still included in the pollen tube dataset. I think I also analyzed non-focal plants initially.
tubes_vials_exp_info02 <- tubes_vials_exp_info %>%
  filter(!(exp_day == "NA" | is.na(exp_day))) %>%
  filter(focal_nf == "focal") %>%
  filter(cover_day != "1") %>% #Only applies to treatment sites
  filter(day_after_cover_day != "1") %>% #Only applies to treatment sites
  filter(!(grepl("open during pre", vial_notes, ignore.case = TRUE) & exp_phase == "post"))
  
#Plants that have data pre and post
plants_to_keep <- tubes_vials_exp_info02 %>%
  group_by(year, patch, plant_species, exp_phase, focal_nf) %>%
  summarise(num_vials = n()) %>%
  pivot_wider(names_from = exp_phase, values_from = num_vials) %>%
  select(year:focal_nf, pre, post) %>%
  filter(pre > 0 & post > 0) %>%
  select(-pre, -post) %>%
  mutate(keep = 1)

tubes_vials_exp_info03 <- tubes_vials_exp_info02 %>%
  left_join(plants_to_keep) %>%
  filter(keep == 1) %>%
  select(-keep)
```

Also remove data that seemed suspect during microscope work

- Data flags currently include situations where I noted that the style was (a) potentially from a different species than the one I thought I was analyzing, (b) a partial style, so there could have been a pollen tube in the missing part, and (c) a test style not meant for analysis.

```{r step4b}
unique(tubes_vials_exp_info03$flag)

tubes_vials_exp_info04 <- tubes_vials_exp_info03 %>%
  filter(is.na(flag) | flag == "NA") %>%
  filter(!is.na(tube_presence))

tubes_for_analysis <- tubes_vials_exp_info04 %>%
  mutate(year_patch = paste(year, patch, sep = "_"))
```

## Step 5: Explore data, part I

How many styles had pollen tubes for each species?

*Note: I focused on analyzing HETO, HAPA, PAV-ROJ-AMA, because I felt most confident about my pollen tube IDs for those species (and because RABO had no pollen tubes).*
```{r step5a, fig.height = 8, fig.width = 12}
presence_plot <- tubes_for_analysis %>%
  ggplot(data = ., aes(x = tube_presence, fill = tube_presence)) +
    geom_histogram(stat = "count") + 
    facet_grid(. ~ plant_species) + 
    labs(x = "Tube presence (0/1)", y = "Number of styles with at least 1 pollen tube", fill = "Tube presence") +
    scale_fill_manual(values = c("red2", "cornflowerblue")) +
    theme_bw(base_size = 18)

presence_plot
```

How many replicates and years represented for each species?
```{r step5b, fig.height = 12, fig.width = 8}
replicate_style_plot <- tubes_for_analysis %>%
  ggplot(data = ., aes(x = year_patch, fill = factor(year), alpha = control_treatment)) +
    geom_histogram(stat = "count", size = 1.25) + 
    facet_grid(plant_species~.) + 
    labs(x = "Replicate", y = "Number of styles analyzed") +
    theme_bw(base_size = 18) +
    scale_fill_manual(values = c("cornflowerblue", "orange", "red2")) +
    scale_alpha_manual(values = c(0.5, 1)) +
    guides(color = guide_legend(override.ae = list(fill = NA))) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
    theme(legend.title = element_blank())

replicate_style_plot
```

## Step 6: Summarize to level of experimental period (pre/post)

```{r step6}
#Proportion of styles with at least one tube - metric used by Hadley et al. 2014, Woods et al. 2022, and I think Kormann et al. as well. Essentially the % of flowers that were pollinated
proportion_pollinated_sum <- tubes_for_analysis %>%
  group_by(plant_species, year, patch, control_treatment, exp_phase, focal_nf, tube_presence) %>%
  summarise(styles = n()) %>%
  ungroup() %>%
  pivot_wider(names_from = tube_presence, values_from = styles, values_fill = 0) %>%
  rename(styles_with_tubes = "1", styles_no_tubes = "0") %>%
  mutate(styles = styles_with_tubes + styles_no_tubes) %>%
  mutate(prop_with_tubes = styles_with_tubes/styles) %>%
  filter(plant_species == "HAPA" | plant_species == "HETO" | plant_species == "PAV-ROJ-AMA" | plant_species == "RABO")

#How many styles ended up in the final sample?
styles_analyzed <- proportion_pollinated_sum %>%
  group_by(plant_species) %>%
  summarise(styles = sum(styles))

styles_analyzed

#Check for complete separation. Are there data for each experimental period, control AND treatment?
styles_analyzed_per_category <- proportion_pollinated_sum %>%
  group_by(plant_species, control_treatment, exp_phase) %>%
  summarise(styles_with_tubes = sum(styles_with_tubes),
            styles_no_tubes = sum(styles_no_tubes))

styles_analyzed_per_category

#Minimum number of total tubes/style. Did not use this method because past researchers in our lab have used the other metric.
# tubes_per_style_sum <- tubes_for_analysis %>%
#   group_by(plant_species, year, patch, control_treatment, exp_phase, focal_nf) %>%
#   summarise(tubes = sum(tubes_total_min, na.rm = TRUE),
#             styles = n()) %>%
#   ungroup() %>%
#   mutate(tubes_per_style = tubes/styles)
```

## Step 7: Explore data, part II

Compare pre/post, control/treatment
```{r step7, fig.height = 5, fig.width = 5}
#Functions to help with plotting
give_n <- function(x){
  
   return(c(y = max(x) + 0.5, label = length(x))) #Multiplier adjusts position
  
}

make_boxplot <- function(dataset, plant_species, yvar, ylabel){
    
    plot <- ggplot(data = dataset, aes(x = control_treatment, y = .data[[yvar]], fill = exp_phase)) +
      geom_boxplot(position = position_dodge(0.85), outlier.shape = NA) +
      geom_point(aes(group = exp_phase), alpha = 0.5, position = position_jitterdodge(dodge.width = 0.85), size = 2) +
      theme_bw(base_size = 18) +
      labs(x = "", y = ylabel, fill = "") +
      ggtitle(plant_species) +
      scale_fill_manual(values = c("cornflowerblue", "red2"))

    return(plot)
    
}

#Proportion of styles with at least one pollen tube
proportion_pollinated_plots <- proportion_pollinated_sum %>% 
  select(plant_species) %>%
  distinct() %>%
  mutate(data = purrr:::map(plant_species, ~filter(proportion_pollinated_sum, plant_species == .x))) %>%
  mutate(plot = purrr:::map2(data, plant_species, ~make_boxplot(dataset = .x, plant_species = .y, yvar = "prop_with_tubes", ylabel = "% flowers pollinated")))

proportion_pollinated_plots$plot

#There are no PAV-ROJ-AMA flowers pollinated in the control 'pre'...this will lead to complete separation in the model and prevent further analysis.
```

## Step 8: Export data
```{r step8}
#Filtered data (unsummarized)
write.csv(tubes_for_analysis, "../../data/export/intermediate/Pollen_tube_data_filtered_for_analysis.csv")

#Summarized data for analysis
write.csv(proportion_pollinated_sum, "../../data/export/for_analysis/Pollen_tube_pollination_success.csv")
```