---
title: "Compiling and visualizing results"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

**Goals**

I have exported the results for each main response variable to rds files, but now I need prepare results for reporting and interpretation.

Specific goals:

1. Create summary tables for each model into an easily exportable table.

2. Calculate contrasts and confidence intervals, and organize them into a table. I want to be able to say: "the pre-to-post change in treatment replicates was X times larger (or smaller) than the pre-to-post change in control replicates (95% CI: X - X times) .

3. Make plots of contrasts in #2. These will be plots for main text.

4. Make plots of estimated marginal means for control/treatment and pre/post (interaction plots)


```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
library(ggeffects)
library(emmeans)
library(ggpubr)
```

```{r}
source("../../code/helper_functions/Modeling_helper_functions.R")
source("../../code/helper_functions/Plotting_helper_functions.R")
source("../../code/helper_functions/Extract_data_from_safely_and_quietly_lists.R")
source("../../code/helper_functions/Calculate_basic_summary_stats.R")
```

## Step 1: Get results (rds files)

```{r}
cameras <- readRDS("../../results/statistical_analysis/rds_files/Camera_results.rds")
captures <- readRDS("../../results/statistical_analysis/rds_files/Capture_results.rds")
telemetry <- readRDS("../../results/statistical_analysis/rds_files/Telemetry_results.rds")
pollen_tubes <- readRDS("../../results/statistical_analysis/rds_files/Pollen_tube_results.rds")
body_mass <- readRDS("../../results/statistical_analysis/rds_files/Body_mass_results.rds")

results <- cameras %>%
  bind_rows(captures) %>%
  bind_rows(telemetry) %>%
  bind_rows(pollen_tubes) %>%
  bind_rows(body_mass) %>%
  select(-model_number) %>% #Model number within a given analysis. Replace with unique #
  mutate(model_number = 1:length(yvar)) %>%
  select(model_number, everything())

#How many total models?
length(results$model_number)

#What non-Heliconia species were analyzed? Plant species scientific names fpr plots
nonheto_species <- read.csv("../../data/export/supp_tables/Non-Heliconia_camera_species_list.csv") %>%
  filter(plant_species %in% results$plant_species) %>%
  select(plant_species, plant_scientific_name, num_replicates)
```

## Step 2: Create model summaries, calculate confidence intervals, and tidy results into dataframe for export

```{r step2, message = FALSE}
#Columns to keep when extract the results
col_names <- c("model_number", "analysis", "subanalysis", "model_type", "bird_group", "plant_species", "yvar")

#Extract model summaries
results_tidy <- results %>%
  select(append(col_names, "summary_tidy")) %>%
  unnest(c(summary_tidy))

#Extract confidence intervals
results_confint <- results %>%
  select(append(col_names, "confint_wald")) %>%
  mutate(confint_df = map(confint_wald, as.data.frame)) %>% #CI as dataframe
  mutate(confint_df = map(confint_df, ~tibble::rownames_to_column(., var = "term"))) %>%
  unnest(cols = confint_df) %>%
  rename(lowerCI = "2.5 %", upperCI = "97.5 %") %>%
  select(-confint_wald, -Estimate)

#Back-transform (exponentiate) coefficients and confidence intervals to data scale from model scale
results_tidy_confint <- results_tidy %>%
  left_join(results_confint) %>%
  mutate_at(vars(estimate, lowerCI, upperCI), .funs = list(exp = ~ifelse(effect == "fixed", exp(.), NA))) %>% 
  mutate_at(vars(estimate, std.error, statistic, lowerCI, upperCI, estimate_exp, lowerCI_exp, upperCI_exp), ~round(., digits = 2)) %>%
  mutate(pvalue_round = format.pval(pv = round(p.value, 3), digits = 3, nsmall = 3, eps = 0.001)) %>%
  select(model_number:term, estimate, lowerCI, upperCI, statistic, pvalue_round, pvalue = p.value, std_error = std.error, everything())

#Extract number of reps for each dataset
sample_size <- results %>%
  filter(model_type == "categorical") %>% #Will be the same for both models; only need oen
  select(append(append(col_names, "num_obs"), "num_reps")) %>%
  unnest(cols = num_reps) %>%
  mutate(num_obs = unlist(num_obs)) %>%
  pivot_wider(names_from = control_treatment, values_from = n)
```

## Step 3: Calculate estimated marginal means for categorical models

```{r}
#For the means and contrasts, will only look at categorical models
results_categorical <- results %>%
  filter(model_type == "categorical")
```

I will use estimated marginal means to visualize and help interpret results. Since I will be plotting these data, I'll use the 'ggeffects' package, which organizes results in a standardized framework.
```{r step 4b, message = FALSE}
#Models for cameras have offset; I want to calculate the number of visits per 12-hour day
emmeans_cameras <- results_categorical %>%
  filter(analysis == "camera_HETO" | analysis == "camera_non-HETO" | analysis == "camera_non-HETO_separate") %>%
  filter(is.na(plant_species) | plant_species != "RABO") %>% #RABO model was weird, fit better with hours as covariate instead of offset
  mutate(ggeffects = map(model, ~ggemmeans(., terms = c("exp_phase", "control_treatment"), back.transform = TRUE, condition = c(hours = 12)))) %>%
  mutate(emmeans = map(model, ~emmeans(., specs = ~exp_phase:control_treatment, type = "response", offset = log(12)))) %>%
  arrange(model_number)

#Check to make sure that offset is being applied correctly; looks like log(offset) is needed for emmeans::emmeans() but not ggeffects::ggmmeans()
emmeans_cameras$ggeffects[[1]]
emmeans_cameras$emmeans[[1]]

#Models for recaps do not have the interaction between treatment and exp_phase
emmeans_recaps <- results_categorical %>%
  filter(subanalysis == "recaptures") %>%
  mutate(ggeffects = map(model, ~ggemmeans(., terms = c("control_treatment"), back.transform = TRUE)))

#Other models
emmeans_other <- results_categorical %>%
  filter(!(model_number %in% emmeans_cameras$model_number) & !(model_number %in% emmeans_recaps$model_number)) %>%
  mutate(ggeffects = map(model, ~ggemmeans(., terms = c("exp_phase", "control_treatment"), back.transform = TRUE)))

#Tibble where each model has a data frame of results to plot
emmeans_for_plots <- emmeans_cameras %>%
  bind_rows(emmeans_recaps) %>%
  bind_rows(emmeans_other) %>%
  select(-emmeans) %>%
  arrange(model_number)

#As data frame
emmeans_df <- emmeans_for_plots %>%
  select(append(col_names, "ggeffects")) %>%
  unnest(ggeffects) %>%
  mutate_if(is.numeric, ~round(., digits = 2))
```

## Step 4: Calculate relevant contrasts

Contrasts will also help with results interpretation, especially for models that include an interaction term. For models with an interaction term, I can calculate two different types of contrasts:

1. pre-to-post change in treatment replicates *AND* pre-to-post change in control replicates (calculated separately)

2. pre-to-post change in treatment replicates *RELATIVE TO* pre-to-post change in control replicates. This is the contrast reflecting the treatment:period interaction term and is a 'contrast of a contrast'.

When interpreting the contrasts, I also need to think about the link function of the model.

**Models with log link**

* Captures (Poisson; # hummingbirds captured)
* Cameras (Poisson/negative binomial; # hummingbird visits)

The default back-transformed contrasts provide *ratios*. These are easy enough to interpret.

**Models with logit link**

* Telemetry (betabinomial; proportion of time spent in focal area)
* Pollen tubes (binomial; proportion of styles with at least one pollen tube)
* Recaptures (binomial; proportion of birds recaptured during 'post' period)

The default back-transformed contrasts provide *odds ratios*. They are OK to interpret, but in this case I want to eventually have contrasts for multiple analyses on the same plot. It might be confusing to mix ratios and odds ratios; ideally I would just have ratios.

The solution to this problem is to calculate ["risk ratios", aka "proportion ratios"](https://github.com/rvlenth/emmeans/issues/48) on the data scale by using emmeans::regrid() and then supplying the 'type="response"' as an argument to confint() or summary().

**Models that don't use a link function**

* Body mass (Gaussian; body mass relative to structural size, i.e., wing length)

```{r step 4, message = FALSE}
#emmeans::confint() gives confidence intervals around contrast
#emmeans::summary() gives p-value for contrast

#CAMERAS AND CAPTURES (log link)
contrasts_cameras_captures <- results_categorical %>%
  filter(analysis == "camera_HETO" | analysis == "camera_non-HETO" | analysis == "camera_non-HETO_separate" | (analysis == "captures" & subanalysis == "captures")) %>%
  mutate(emm = map(model, ~emmeans(., specs = ~exp_phase:control_treatment))) %>%
  mutate(contrast = map(emm, ~as.data.frame(confint(contrast(., method = "revpairwise", by = c("control_treatment")), type = "response")))) %>%
  mutate(contrast_of_contrast = map(emm, ~as.data.frame(confint(contrast(emmeans(., specs = ~exp_phase:control_treatment), interaction = ("revpairwise")), type = "response")))) %>%
  mutate(contrast_pval_check = map(emm, ~summary(contrast(emmeans(., specs = ~exp_phase:control_treatment), interaction = ("revpairwise")), type = "response")))

#TELEMETRY AND POLLEN TUBES (logit link)
contrasts_telemetry_pollen_tubes <- results_categorical %>%
  filter(analysis == "telemetry" | analysis == "pollen_tubes") %>%
  mutate(emm = map(model, ~emmeans(., specs = ~exp_phase:control_treatment))) %>%
  mutate(emm_regrid = map(emm, ~regrid(., transform = "log"))) %>%
  mutate(contrast = map(emm_regrid, ~as.data.frame(confint(contrast(., interaction = "revpairwise", by = c("control_treatment")), type = "response")))) %>%
  mutate(contrast_of_contrast = map(emm_regrid, ~as.data.frame(confint(contrast(emmeans(., specs = ~exp_phase:control_treatment), interaction = "revpairwise"), type = "response")))) %>%
  mutate(contrast_pval_check = map(emm_regrid, ~summary(contrast(emmeans(., specs = ~exp_phase:control_treatment), interaction = "revpairwise"), type = "response")))

#RECAPTURES (logit link, but don't have the treatment x period interaction)
contrasts_recaps <- results_categorical %>%
  filter(subanalysis == "recaptures") %>%
  mutate(emm = map(model, ~emmeans(., specs = ~control_treatment))) %>%
  mutate(emm_regrid = map(emm, ~regrid(., transform = "log"))) %>%
  mutate(contrast = map(emm_regrid, ~as.data.frame(confint(contrast(., interaction = "revpairwise"), type = "response")))) %>%
  mutate(contrast_pval_check = map(emm_regrid, ~summary(contrast(., interaction = "revpairwise"), type = "response")))

#BODY MASS (Gaussian, so change will be relative to ZERO, not 1)
contrasts_body_mass <- results_categorical %>%
  filter(subanalysis == "body_mass") %>%
  mutate(emm = map(model, ~emmeans(., specs = ~exp_phase:control_treatment))) %>%
  mutate(contrast = map(emm, ~as.data.frame(confint(contrast(., by = c("control_treatment"), method = "revpairwise"))))) %>%
  mutate(contrast_of_contrast = map(emm, ~as.data.frame(confint(contrast(., interaction = c("revpairwise", "revpairwise")))))) %>%
  mutate(contrast_of_contrast = map(contrast_of_contrast, ~rename(., ratio = estimate))) #Rename column to match other analyses, but note that it's not actually a ratio!

contrasts_body_mass$contrast
contrasts_body_mass$contrast_of_contrast

#Combine
#Pre-to-post change, control and treatment replicates separately
contrasts <- contrasts_cameras_captures %>%
  bind_rows(contrasts_telemetry_pollen_tubes) %>%
  bind_rows(contrasts_body_mass)

#Contrasts reflecting the coefficient of interest (interaction term for all analyses except recaptures)
contrasts_of_contrasts <- contrasts_recaps %>%
  rename(contrast_of_contrast = contrast) %>%
  bind_rows(contrasts_cameras_captures) %>%
  bind_rows(contrasts_telemetry_pollen_tubes) %>%
  bind_rows(contrasts_body_mass)
```

```{r, include = FALSE, eval = FALSE}
#Check: compare p-value of coefficient of interest to p-value with contrast of interest; they should be pretty close
results_categorical %>% filter(model_number == 1) %>% pull(summary)
contrasts_of_contrasts %>% filter(model_number == 1) %>% pull(contrast_pval_check)                                
                                 
results_categorical %>% filter(model_number == 17) %>% pull(summary)
contrasts_of_contrasts %>% filter(model_number == 17) %>% pull(contrast_pval_check) 

results_categorical %>% filter(model_number == 29) %>% pull(summary)
contrasts_of_contrasts %>% filter(model_number == 29) %>% pull(contrast_pval_check)

results_categorical %>% filter(model_number == 33) %>% pull(summary)
contrasts_of_contrasts %>% filter(model_number == 33) %>% pull(contrast_pval_check)

results_categorical %>% filter(model_number == 21) %>% pull(summary)
contrasts_of_contrasts %>% filter(model_number == 21) %>% pull(contrast_pval_check)
```

Extract contrast results
```{r step4d, messsage = FALSE}
#Contrasts for control and treatment replicates separately
contrasts_df <- contrasts %>%
  select(append(col_names, "contrast")) %>%
  unnest(contrast) %>%
  arrange(model_number) %>%
  mutate_if(is.numeric, ~round(., digits = 2)) %>%
  mutate(contrast = ifelse(is.na(contrast), as.character(exp_phase_revpairwise), as.character(contrast))) %>%
  select(-exp_phase_revpairwise) %>%
  select(model_number:contrast, control_treatment, ratio, lower.CL, upper.CL, everything())

#Contrasts for treatment effect; for specialization models, this is the contrast representing the interaction term (contrast of contrasts)
contrasts_of_contrasts_df <- contrasts_of_contrasts %>%
  select(append(col_names, "contrast_of_contrast")) %>%
  unnest(contrast_of_contrast) %>%
  arrange(model_number) %>%
  mutate_if(is.numeric, ~signif(., digits = 2)) %>%
  select(model_number:starts_with("control_treatment"), starts_with("exp_phase"), ratio, lower.CL, upper.CL, everything())
```

## Step 5: Plot results

There are two ways that I like to visualize the interaction term of interest

1. Interaction plots, with estimated marginal means for control/treatment and pre/post (pre and post values connected by lines)

- These interaction plots can be confusing without detailed explanation, so they will only be for supplemental information.
- Not for analysis of recapture rate, since those models do not have an interaction term.

2. Contrast plots, with contrast reflecting the interaction term and its associated confidence intervals

- These is the key plot for the main text

**Make interaction plots**
```{r step5a, message = FALSE, fig.width=9, fig.height=9}
#Calculate max values for each response variable
#If want to have common axis scaling across variables that will be in same plot, can group again and take max across those variables
max_values <- emmeans_df %>%
  group_by(analysis, subanalysis, plant_species) %>%
  summarise(ymax = round(max(conf.high) + 0.5, 0)) %>%
  ungroup() %>%
  mutate(ymin = 0) %>%
  mutate(ybreak = 1) %>%
  mutate(yaccuracy = 1)

#Adjust axis limits and breaks as needed (NOTE: body mass plot was kind of complicated so tailored it in function)
#Make a bunch of plots
interaction_plots <- emmeans_for_plots %>%
  filter(subanalysis != "recaptures") %>%
  left_join(max_values) %>%
  mutate(ymax = ifelse(analysis == "camera_non-HETO" & subanalysis == "all_birds" & bird_group == "greh_visa", 1, ymax)) %>%
  mutate(ybreak = ifelse(analysis == "camera_HETO" & subanalysis == "all_birds", 3, ybreak)) %>%
  mutate(ybreak = ifelse(analysis == "pollen_tubes" | analysis == "telemetry", 25, ybreak)) %>%
  mutate(ybreak = ifelse(analysis == "captures" & subanalysis == "captures", 3, ybreak)) %>%
  mutate(interaction_plot = pmap(list(ggeffects, yvar, ymin, ymax, ybreak, yaccuracy), ~make_interaction_plot(ggeffects_df = ..1, yvar = ..2, ymin = ..3, ymax = ..4, ybreak = ..5, yaccuracy = ..6, as_percent = TRUE)))

#interaction_plots %>% filter(model_number == 33) %>% pull(interaction_plot)
```

**Divide up interaction plots into reasonably sized panel figures**
```{r}
#CAMERAS (ALL BIRDS)
interaction_plots_cameras_all <- interaction_plots %>%
  filter(analysis == "camera_HETO" | analysis == "camera_non-HETO") %>%
  filter(subanalysis == "all_birds") %>%
  arrange(yvar, analysis, bird_group)

interaction_multiplot_cameras_all <- ggarrange(plotlist = interaction_plots_cameras_all$interaction_plot, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom", align = "hv", labels = "AUTO", font.label = list(size = 16, face = "plain"))
interaction_multiplot_cameras_all

#CAMERAS (MARKED BIRDS)
interaction_plots_cameras_marked <- interaction_plots %>%
  filter(analysis == "camera_HETO" | analysis == "camera_non-HETO") %>%
  filter(subanalysis == "marked_birds") %>%
  arrange(yvar, analysis, bird_group)

interaction_multiplot_cameras_marked <- ggarrange(plotlist = interaction_plots_cameras_marked$interaction_plot, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom", align = "hv", labels = "AUTO", font.label = list(size = 16, face = "plain"))
interaction_multiplot_cameras_marked

#CAPTURES + TELEMETRY
interaction_plots_captures_telemetry <- interaction_plots %>%
  filter(analysis == "captures" | analysis == "telemetry") %>%
  filter(subanalysis != "all_replicates") %>%
  arrange(yvar, analysis, bird_group)

interaction_multiplot_captures_telemetry <- ggarrange(plotlist = interaction_plots_captures_telemetry$interaction_plot, nrow = 2, ncol = 2, common.legend = TRUE, legend = "bottom", align = "hv", labels = "AUTO", font.label = list(size = 16, face = "plain"))
interaction_multiplot_captures_telemetry

#POLLEN TUBES
interaction_plots_pollination <- interaction_plots %>%
  filter(analysis == "pollen_tubes") %>%
  mutate(subanalysis = factor(subanalysis, levels = c("HETO", "HAPA"), ordered = TRUE)) %>%
  arrange(yvar, subanalysis)

interaction_multiplot_pollination <- ggarrange(plotlist = interaction_plots_pollination$interaction_plot, nrow = 1, ncol = 2, common.legend = TRUE, legend = "bottom", align = "hv", labels = "AUTO", font.label = list(size = 16, face = "plain"))
interaction_multiplot_pollination

#BODY MASS
interaction_plots_body_mass <- interaction_plots %>%
  filter(analysis == "body_mass") %>%
  arrange(yvar, analysis)

interaction_multiplot_body_mass <- ggarrange(plotlist = interaction_plots_body_mass$interaction_plot, nrow = 1, ncol = 2, common.legend = TRUE, legend = "bottom", align = "hv", labels = "AUTO", font.label = list(size = 16, face = "plain"))
interaction_multiplot_body_mass
```

**Contrast plots**

When making interaction plots, I had one plot per model. Here, I want to combine multiple models per plot, so I'll just do the combinations by hand.

First, I need to get the labels sorted out.
```{r}
#Labels with same-sized text in each line, following: https://stackoverflow.com/questions/40577023/r-ggplot-annotated-with-atop-using-three-values-and-bgroup
#textstyle(x)	draw x in normal size
#scriptstyle(x)	draw x in small size
#scriptscriptstyle(x)	draw x in very small size

#How to have 3-line label:
#3lineexample <- c(expression(atop(bold("Flower visitation"), atop(textstyle("visits/hr"), atop(scriptscriptstyle(""), scriptstyle("(focal"~italic(Heliconia)*")"))))))

#Only need labels when there are x-axis tick marks
camera_heto_label <- c(expression("focal"~italic(Heliconia)))
camera_nonheto_label <- c(expression(atop("non-"*italic(Heliconia)~"species ("*italic(N)*"=30)")))

camera_heto_marked_label <- c(expression("focal"~italic(Heliconia)))
camera_nonheto_marked_label <- c(expression(atop("non-"*italic(Heliconia)~"species ("*italic(N)*"=17)")))

pollination_heto_label <- c(expression("focal"~italic(Heliconia)))
pollination_hapa_label <- c(expression(italic(Hamelia)~italic(patens)))

camera_nonheto_separate_title <- c(expression("Flower visitation to individual non-"*italic(Heliconia)~"species (visits/hr)"))
```

```{r}
#CAPTURES
contrast_plot_captures <- contrasts_of_contrasts_df %>%
  filter((analysis == "captures" & subanalysis == "captures")) %>%
  mutate(analysis = factor(analysis, levels = c("captures"), ordered = TRUE)) %>%
  arrange(analysis) %>%
  mutate(analysis_id = paste(analysis, subanalysis, sep = "_")) %>%
  make_contrast_plot(contrasts_df = ., xvar = "analysis_id") +
    scale_y_continuous(limits = c(0, 2), breaks = c(0, 0.5, 1, 2)) +
    coord_cartesian(ylim = c(0, 2), xlim = c(1, 1), clip = "off") +
    theme(legend.position = "bottom", legend.justification = c(0.5)) +
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
    labs(title = "Abundance (# hummingbirds captured)")

contrast_plot_captures

#TELEMETRY
contrast_plot_telemetry <- contrasts_of_contrasts_df %>%
  filter(analysis == "telemetry" & subanalysis == "all_replicates") %>%
  mutate(analysis = factor(analysis, levels = c("telemetry"), ordered = TRUE)) %>%
  arrange(analysis) %>%
  mutate(analysis_id = paste(analysis, subanalysis, sep = "_")) %>%
  make_contrast_plot(contrasts_df = ., xvar = "analysis_id") +
    scale_y_continuous(limits = c(0, 2), breaks = c(0, 0.5, 1, 2)) +
    coord_cartesian(ylim = c(0, 2), xlim = c(1, 1), clip = "off") +
    theme(legend.position = "bottom", legend.justification = c(0.5)) +
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
    labs(title = "Space use (% time spent in focal area)")

contrast_plot_telemetry

#FLOWER VISITATION: Cameras (HETO and non-HETO)
contrast_plot_flower_visits <- contrasts_of_contrasts_df %>%
  filter((analysis == "camera_HETO" & subanalysis == "all_birds") |
           (analysis == "camera_non-HETO" & subanalysis == "all_birds")) %>%
  mutate(analysis = factor(analysis, levels = c("camera_HETO", "camera_non-HETO"), ordered = TRUE)) %>%
  arrange(analysis) %>%
  mutate(analysis_id = paste(analysis, subanalysis, sep = "_")) %>%
  make_contrast_plot(contrasts_df = ., xvar = "analysis_id") +
    scale_x_discrete(labels = c(camera_heto_label, camera_nonheto_label)) +
    scale_y_continuous(limits = c(0, 3), breaks = c(0, 0.5, 1, 2, 3)) +
    coord_cartesian(ylim = c(0, 3), xlim = c(1, 2), clip = "off") +
    theme(legend.position = "bottom", legend.justification = c(0.5)) +
    labs(title = "Flower visitation (visits/hr)")
    
contrast_plot_flower_visits

#POLLINATION SUCCESS
contrast_plot_pollination <- contrasts_of_contrasts_df %>%
  filter(analysis == "pollen_tubes") %>%
  mutate(subanalysis = factor(subanalysis, levels = c("HETO", "HAPA"), ordered = TRUE)) %>%
  arrange(subanalysis) %>%
  mutate(analysis_id = paste(analysis, subanalysis, sep = "_")) %>%
  make_contrast_plot(contrasts_df = ., xvar = "analysis_id") +
    scale_x_discrete(labels = c(pollination_heto_label, pollination_hapa_label)) +
    scale_y_continuous(limits = c(0, 7), breaks = c(0, 0.5, 1, 2, 3, 4, 5, 6, 7)) +
    coord_cartesian(ylim = c(0, 7), xlim = c(1, 2), clip = "off") +
    theme(legend.position = "none") +
    labs(title = "Pollination success (% flowers pollinated)")

contrast_plot_pollination

#VISTATION TO INDIVIDUAL NON-HETO PLANT SPECIES
contrast_plot_nonheto <-  contrasts_of_contrasts_df %>%
  filter(analysis == "camera_non-HETO_separate") %>%
  left_join(nonheto_species) %>%
  mutate(plant_scientific_name = forcats::fct_reorder(plant_scientific_name, num_replicates)) %>%
  arrange(desc(plant_scientific_name)) %>%
  make_contrast_plot(contrasts_df = ., xvar = "plant_scientific_name") +
    scale_y_continuous(limits = c(0, 3), breaks = c(0, 0.5, 1, 2, 3)) +
    coord_cartesian(ylim = c(0, 3), xlim = c(1, 9), clip = "off") +
    theme(legend.position = "bottom") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, face = "italic")) +
    labs(title = camera_nonheto_separate_title)
   
contrast_plot_nonheto

#RECAPTURES
contrast_plot_recaps <- contrasts_of_contrasts_df %>%
  filter(analysis == "captures" & subanalysis == "recaptures") %>%
  mutate(analysis = factor(analysis, levels = c("captures"), ordered = TRUE)) %>%
  arrange(analysis) %>%
  mutate(analysis_id = paste(analysis, subanalysis, sep = "_")) %>%
  make_contrast_plot(contrasts_df = ., xvar = "analysis_id") +
    scale_y_continuous(limits = c(0, 3), breaks = c(0, 0.5, 1, 2, 3)) +
    coord_cartesian(ylim = c(0, 3), xlim = c(1, 1), clip = "off") +
    theme(legend.position = "bottom", legend.justification = c(0.5)) +
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
    labs(title = "Recapture probability (% of birds recaptured)")

contrast_plot_recaps

#MARKED BIRDS
contrast_plot_marked <- contrasts_of_contrasts_df %>%
  filter((analysis == "camera_HETO" & subanalysis == "marked_birds") |
           (analysis == "camera_non-HETO" & subanalysis == "marked_birds")) %>%
  mutate(analysis = factor(analysis, levels = c("camera_HETO", "camera_non-HETO"), ordered = TRUE)) %>%
  arrange(analysis) %>%
  mutate(analysis_id = paste(analysis, subanalysis, sep = "_")) %>%
  make_contrast_plot(contrasts_df = ., xvar = "analysis_id") +
    scale_x_discrete(labels = c(camera_heto_marked_label, camera_nonheto_marked_label)) +
    scale_y_continuous(limits = c(0, 2), breaks = c(0, 0.5, 1, 2)) +
    coord_cartesian(ylim = c(0, 2), xlim = c(1, 2), clip = "off") +
    theme(legend.position = "bottom", legend.justification = c(0.5)) +
    labs(title = "Flower visitation from marked birds (visits/hr)")

contrast_plot_marked

#BODY MASS
contrast_plot_body_mass <- contrasts_of_contrasts_df %>%
  filter(analysis == "body_mass") %>%
  arrange(analysis) %>%
  mutate(analysis_id = paste(analysis, subanalysis, sep = "_")) %>%
  make_contrast_plot(contrasts_df = ., xvar = "analysis_id") +
    scale_y_continuous(limits = c(-0.10, 0.10)) +
    coord_cartesian(ylim = c(-0.10, 0.10), xlim = c(1, 1), clip = "off") +
    theme(legend.position = "bottom", legend.justification = c(0.5)) +
    theme(axis.ticks.x = element_blank(), axis.text.x = element_blank()) +
    labs(title = "Bird condition (relative body mass)")

contrast_plot_body_mass
```

Combine contrast plots in various ways for publication
```{r, fig.width = 13, fig.height = 6.5}
#Results for captures and telemetry. 2 panel plot; left = captures, right = telemetry
contrast_multiplot_captures_telemetry <- ggarrange(contrast_plot_captures, contrast_plot_telemetry, common.legend = TRUE, ncol = 2, nrow = 1, align = "hv", legend = "bottom", widths = c(1, 1), labels = c("A", "B"), font.label = list(size = 28, face = "plain"))

contrast_multiplot_captures_telemetry
```

```{r, fig.width = 13, fig.height = 13}
#Results for flower visitation and pollination success. 3-panel plot; upper panel = cameras (HETO, non-HETO overall) and pollinatio, lower panel = individual non-HETO species
contrast_multiplot_cameras_poll_upper <- ggarrange(contrast_plot_flower_visits, contrast_plot_pollination, ncol = 2, nrow = 1, align = "hv", legend = "none", widths = c(1, 1), labels = c("A", "B"), font.label = list(size = 28, face = "plain"))

contrast_multiplot_cameras_poll_upper

contrast_multiplot_cameras_poll_lower <- ggarrange(contrast_plot_nonheto, labels = c("C"), font.label = list(size = 28, face = "plain"))
contrast_multiplot_cameras_poll_lower

contrast_multiplot_cameras_poll <- ggarrange(contrast_multiplot_cameras_poll_upper, contrast_multiplot_cameras_poll_lower, ncol = 1, nrow = 2, common.legend = TRUE, legend = "bottom")
contrast_multiplot_cameras_poll
```

```{r, fig.width = 7, fig.height = 13}
#Results for "additional response variables". 3-panel plot; upper panel = recaptures, middle panel = flower visitation from marked birds, lower panel = body mass
contrast_multiplot_addl_analyses <- ggarrange(contrast_plot_recaps, contrast_plot_marked, contrast_plot_body_mass,
                                              common.legend = TRUE, ncol = 1, nrow = 3, align = "hv", legend = "bottom", labels = c("A", "B", "C"), font.label = list(size = 28, face = "plain"))
                                              
  
contrast_multiplot_addl_analyses
```

## Step 6: Export results 
```{r}
#SUMMARY TABLES
path_name <- c("../../results/statistical_analysis/tables")
write.csv(results_tidy_confint, file.path(path_name, "Hummingbird_persistence_results_summary_tables.csv"))
write.csv(sample_size, file.path(path_name, "Hummingbird_persistence_results_sample_size_summary.csv"))
write.csv(emmeans_df, file.path(path_name,"Hummingbird_persistence_results_emmeans.csv"))
write.csv(contrasts_df, file.path(path_name,"Hummingbird_persistence_results_contrasts.csv"))
write.csv(contrasts_of_contrasts_df, file.path(path_name, "Hummingbird_persistence_results_contrasts_of_contrasts.csv"))

#FIGURES
path_name <- c("../../results/statistical_analysis/figures")

#For supplement
ggsave(file.path(path_name, "Interaction_multiplot_captures_telemetry.png"), interaction_multiplot_captures_telemetry, dpi = 300, units = "in", width = 9, height = 9, bg = "white")
ggsave(file.path(path_name, "Interaction_multiplot_cameras_all_birds.png"), interaction_multiplot_cameras_all, dpi = 300, units = "in", width = 9, height = 9, bg = "white")
ggsave(file.path(path_name, "Interaction_multiplot_cameras_marked_birds.png"), interaction_multiplot_cameras_marked, dpi = 300, units = "in", width = 9, height = 9, bg = "white")
ggsave(file.path(path_name, "Interaction_multiplot_pollination.png"), interaction_multiplot_pollination, dpi = 300, units = "in", width = 9, height = 6, bg = "white")
ggsave(file.path(path_name, "Interaction_multiplot_body_mass.png"), interaction_multiplot_body_mass, dpi = 300, units = "in", width = 9, height = 6, bg = "white")

#For main text
ggsave(file.path(path_name, "Contrast_plot_captures_telemetry.png"), contrast_multiplot_captures_telemetry, dpi = 300, units = "in", width = 13, height = 6.5, bg = "white")
ggsave(file.path(path_name, "Contrast_multiplot_cameras_pollination.png"), contrast_multiplot_cameras_poll, dpi = 300, units = "in", width = 13, height = 13, bg = "white")
ggsave(file.path(path_name, "Contrast_multiplot_addl_analyses.png"), contrast_multiplot_addl_analyses, dpi = 300, units = "in", width = 7, height = 13, bg = "white")
```

