---
title: "Analyzing visit duration"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

This is an extra analysis added during peer review.

**Goal:** 

Explore whether there was an experimental effect on sighting length (aka "visit duration"), under the hypothesis that hummingbirds visited flowers longer after *Heliconia* removal to gain additional calories. This behavioral response would be undetected by the primary response variables.

```{r setup, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

#Packages for statistical modeling
library(glmmTMB)
library(AICcmodavg)
library(DHARMa)
library(emmeans)
library(ggeffects)

#Packages for data wrangling
library(dplyr)
library(tidyr)
library(lubridate)
library(purrr)

#Packages for plotting
library(ggplot2)
library(ggrepel)
library(ggpubr)

#Set up parallel processing (likelihood profile CI take forever to run!)
library(future)
plan(multisession)

#Set seed
set.seed(1)
```

## Step 1: Get data

Have already filtered data for analysis in previous script, '02_filtering_summarizing_camera_data'.

Will do some additional filtering here to remove instances of a bird perching on the plant, which would generate extra long sighting ("visit") durations.

Also, some camera sets had >1 plant species in the frame, but the sighting length is for ALL plant species combined. Will not analyze these sightings, because interpretation is a bit awkward; can not interpret results as time spent at each inflorescence of a given plant species. Also, if I keep these sightings, there would be a mismatch between sighting length (for >1 plant species) and the flowers covariate (counted for each plant species).
```{r}
##Get data
data_for_experiment <- read.csv("data/export/intermediate/Camera_data_filtered_for_experiment.csv")

##Source helper functions
source("code/helper_functions/Calculate_basic_summary_stats.R")
source("code/helper_functions/Summarize_camera_data.R")
source("code/helper_functions/Modeling_helper_functions.R")

##Filter out camera sets with >1 plant species
##Filter out instances of bird perching in frame, based on notes column
single_species_camera_sets <- data_for_experiment %>%
  distinct(year, patch, camera_num, plant_species) %>%
  group_by(year, patch, camera_num) %>%
  summarise(num_species = n()) %>%
  filter(num_species == 1)

data_for_sighting_duration <- data_for_experiment %>%
  left_join(single_species_camera_sets) %>%
  filter(num_species == 1) %>%
  select(-num_species, -X) %>%
  filter(!grepl("perch", sighting_notes, ignore.case = TRUE)) %>%
  filter(sightings_yes_or_no == "Y") %>%
  mutate(year_patch = paste(year, patch, sep = "_")) %>%
  mutate(exp_phase = factor(exp_phase, levels = c("pre", "post")))
```

## Step 2: Explore data

What is average sighting length?
```{r}
#Time per sighting (in seconds) - across all bird and plant species
data_for_sighting_duration %>%
  calculate_basic_summary_stats(variable = sighting_length)

#PLOT: Time per sighting (in seconds) - across all bird and plant species
data_for_sighting_duration %>%
  ggplot(aes(x = sighting_length), data = .) +
    geom_histogram(binwidth = 1, center = 0) +
    theme_bw(base_size = 18) +
    labs(x = "Time per sighting (seconds)", y = "Count")
```

```{r, include = FALSE}
# Create test data for checking/troubleshooting
test_data <- data_for_sighting_duration %>%
  filter(!is.na(flowers_camera_video))

# Model without summarizing data (i.e., 1 row = 1 sighting)
test_model <- glmmTMB::glmmTMB(sighting_length ~ control_treatment * exp_phase + log(flowers_camera_video) + (1|patch/year_patch/plant_species), data = test_data, na.action = na.omit, family = "truncated_genpois")

simulationOutput <- simulateResiduals(fittedModel = test_model)
plot(simulationOutput)
plotResiduals(simulationOutput, test_data$control_treatment)
plotResiduals(simulationOutput, test_data$exp_phase)
plotResiduals(simulationOutput, as.numeric(test_data$flowers_camera_video))

#Test for 1-inflation and 2-inflation, from DHARMa: https://cran.r-project.org/web/packages/DHARMa/vignettes/DHARMa.html#zero-inflation-k-inflation-or-deficits
countOnes <- function(x) sum(x == 1)  # testing for number of 1s
testGeneric(simulationOutput, summary = countOnes, alternative = "greater") # "greater" = 1-inflation

countTwos <- function(x) sum(x == 2)  # testing for number of 2s
testGeneric(simulationOutput, summary = countTwos, alternative = "greater") # "greater" = 2-inflation

countThrees <- function(x) sum(x == 3)  # testing for number of 3s
testGeneric(simulationOutput, summary = countThrees, alternative = "greater") # "greater" = 3-inflation

countFours <- function(x) sum(x == 4)  # testing for number of 4s
testGeneric(simulationOutput, summary = countFours, alternative = "greater") # "greater" = 4-inflation

countFives <- function(x) sum(x == 5)  # testing for number of 5s
testGeneric(simulationOutput, summary = countFives, alternative = "greater") # "greater" = 5-inflation

#Have more ones, twos, threes, and fours than expected...
```

## Step 3: Summarize data

These are the same summaries for visitation rate analyses, *except* that I am using a dataset that has sightings with perching filtered out.
```{r}
sighting_durations_all_spp = calculate_sighting_rates(data = data_for_sighting_duration, level_org = "plant_species", level_time = "exp_phase", level_bird = "camera_spp_combined", sightings = "with_visit", include_unknown_spp = FALSE) %>%
  mutate(bird_group = "all_spp") #Replace "camera_spp_combined" with "all_spp"

sighting_durations_greh_visa = calculate_sighting_rates(data = data_for_sighting_duration, level_org = "plant_species", level_time = "exp_phase", level_bird = list(greh_visa = c("GREH", "VISA")), sightings = "with_visit", include_unknown_spp = FALSE)
 
#Combine various summaries
sighting_durations <- sighting_durations_all_spp %>%
  bind_rows(sighting_durations_greh_visa) %>%
  select(bird_group, everything()) %>%
  mutate(time_per_sighting = sightings_time/sightings) #Time is in seconds
```

Not all plants have sightings pre and post; can only analyze changes in sighting duration if both experimental periods have sightings, so need to remove plant species that do not have sightings pre and post
```{r}
#Identify plant species that have sightings for both experimental periods
species_pre_and_post <- sighting_durations %>%
  filter(!is.na(sightings_time)) %>%
  distinct(bird_group, year, patch, control_treatment, plant_species, exp_phase) %>%
  group_by(bird_group, year, patch, control_treatment, plant_species) %>%
  summarise(num_periods = n()) %>%
  ungroup() %>%
  filter(num_periods == 2)

sighting_durations_for_analysis <- sighting_durations %>%
  left_join(species_pre_and_post) %>%
  filter(num_periods == 2) %>%
  select(-num_periods) %>%
  mutate(year_patch = paste(year, patch, sep = "_")) %>%
  mutate(exp_phase = factor(exp_phase, levels = c("pre", "post")))

#Check: are there any NAs in the sighting_duration column?
check01 <- sighting_durations_for_analysis %>%
  filter(is.na(sightings_time))
```

## Step 4: Analyze data

If follow framework used in rest of analyses, I would have 4 models:

1. Heliconia tortuosa (HETO), All hummingbird species
2. Heliconia tortuosa (HETO), Green hermits and Violet sabrewings (Heliconia specialists)
3. All non-HETO plant species, All hummingbird species
4. All non-HETO plant species, Green hermits and Violet sabrewings (Heliconia specialists)

However, here the question is not about visitation rates to HETO vs. non-HETO, so I will analyze all plant species together for simplicity. This approach yields 2 models:

1. All plant species, All hummingbird species
2. All plant species, Green hermits and Violet sabrewings (Heliconia specialists)

**Model fitting**

For count data, there multiple possible distributions. I need to choose between Poisson and negative binomial (nbinom1 and nbinom2). Also, because the dataset does not include zeroes, I need a truncated distribution.

ALL HUMMINGBIRD SPECIES
```{r}
data_all_spp <- sighting_durations_for_analysis %>%
  filter(bird_group == "all_spp")

m1 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_all_spp, na.action = na.omit, family = "truncated_poisson")

m2 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_all_spp, na.action = na.omit, family = "truncated_nbinom1")

m3 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_all_spp, na.action = na.omit, family = "truncated_nbinom2")

m4 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_all_spp, na.action = na.omit, family = "truncated_genpois")

m5 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_all_spp, na.action = na.omit, family = "poisson")

m6 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_all_spp, na.action = na.omit, family = "nbinom1")

m7 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_all_spp, na.action = na.omit, family = "nbinom2")

m8 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_all_spp, na.action = na.omit, family = "genpois")

#Combine models
model_fitting01 <- tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6", "m7", "m8"), model = list(m1, m2, m3, m4, m5, m6, m7, m8)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting01 %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Check to make sure assumptions look OK
#The models with the lowest AICc actually do not look great. nbinom2 (m7) is best in terms of DHARMa plots
model_fitting01$dharma_plot[[7]]
model_fitting01$dharma_overdisp_plot[[7]]

model_fitting01$model[[7]] %>% summary()

#Assumptions do not look great...would a normal distribution work?
gaussian_model <- glmmTMB::glmmTMB(time_per_sighting ~ control_treatment * exp_phase + log(flowers) + (1|patch/year_patch/plant_species), data = data_all_spp, na.action = na.omit, family = "gaussian")
simulateResiduals(gaussian_model) %>% plot()

#Nope, looks even worse...
```

HELICONIA SPECIALISTS
```{r}
data_greh_visa <- sighting_durations_for_analysis %>%
  filter(bird_group == "greh_visa")

m1 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_greh_visa, na.action = na.omit, family = "truncated_poisson")

m2 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_greh_visa, na.action = na.omit, family = "truncated_nbinom1")

m3 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_greh_visa, na.action = na.omit, family = "truncated_nbinom2")

m4 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_greh_visa, na.action = na.omit, family = "truncated_genpois")

m5 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_greh_visa, na.action = na.omit, family = "poisson")

m6 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_greh_visa, na.action = na.omit, family = "nbinom1")

m7 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_greh_visa, na.action = na.omit, family = "nbinom2")

m8 <- glmmTMB::glmmTMB(sightings_time ~ control_treatment * exp_phase + log(flowers) + offset(log(sightings)) + (1|patch/year_patch/plant_species), data = data_greh_visa, na.action = na.omit, family = "genpois")

#Combine models
model_fitting02 <- tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6", "m7", "m8"), model = list(m1, m2, m3, m4, m5, m6, m7, m8)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting02 %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Check to make sure assumptions look OK
#The models with the lowest AICc actually do not look great. genpois (m8) is best in terms of DHARMa plots
model_fitting02$dharma_plot[[8]]
model_fitting02$dharma_overdisp_plot[[8]]

#Summary
model_fitting02$model[[8]] %>% summary()
```