---
title: "Making maps of study area"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---


**Goal**

Make maps illustrating the following:

- The overall study area + sites in which we worked (relative to Las Cruces Biological Station)

- The location of Las Cruces Biological Station within Costa Rica/central America

- The concept of a "focal area" within a site

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

library(tidyr)
library(purrr)
library(ggplot2)

#Spatial packages
library(sf)
library(sp)
library(tmap)
library(rnaturalearth)

library(dplyr) #load last so that 'select' function does not get masked

#Set up parallel processing
library(future)
plan(multisession)

raster::removeTmpFiles(h=0) #this removes all files. If h = 24, removes all temp files more than 24 hours old, etc.
```

## Step 1: Import data

Experiment data
```{r}
#Make variable indicating paired sites
exp_info <- read.csv("data/import/Experiment_dates_2016-2018.csv") %>%
  mutate(replicate_id = paste(year, replicate, sep = "_")) %>%
  distinct(year, patch, replicate_id) %>%
  rename(replicate = replicate_id) %>%
  mutate_all(as.character)
```

Site markers and focal area outlines
```{r}
#Focal area outlines
focal_areas <- sf::st_read("data/export/intermediate/focal_areas_2016-2018.shp")
focal_areas <- sf::st_transform(focal_areas, crs = 32617) #crs code was somehow lost during export to shapefile. Re-adding here...

proj <- st_crs(focal_areas) #projection. can use this throughout script as needed

#Site markers (focal area centroids)
centroids <- read.csv("data/export/intermediate/Focal_area_sizes_and_centroids.csv") %>%
  select(-X, -id) %>%
  mutate_all(as.character) %>%
  left_join(exp_info)

centroids_spatial <- st_as_sf(centroids, coords = c("x", "y"))
centroids_spatial <- st_set_crs(centroids_spatial, value = proj)

#For sites used in multiple years, take average
mean_centroids <- centroids %>%
  group_by(patch) %>%
  summarise(x = mean(as.numeric(x)),
            y = mean(as.numeric(y)))

mean_centroids_spatial <- st_as_sf(mean_centroids, coords = c("x", "y"))
mean_centroids_spatial <- st_set_crs(mean_centroids_spatial, value = proj)
```

Net and camera locations
```{r}
#Nets
nets <- read.csv("data/import/Nets_2016-2018_20210909.csv") %>%
 distinct(year, patch, net_number, net_length, x_utm, y_utm) %>%
 arrange(year, patch, net_number) %>%
 filter(!is.na(x_utm) & !is.na(y_utm)) #remove NAs. 'st_as_sf' cannot handle NAS

nets_spatial <- st_as_sf(nets, coords = c("x_utm", "y_utm"))
nets_spatial <- st_set_crs(nets_spatial, value = proj)

#Cameras
cameras <- read.csv("data/import/Camera_locations_2016-2018_20210705.csv") %>%
 filter(!is.na(x) & !is.na(y)) #remove NAs for coordinates.'st_as_sf' cannot handle NAS

#Cameras at stations (2/site). Some sites have multiple coordinates per station (one per camera). Take average x-y coordinates.
cameras_stations <- cameras %>%
    filter(station == 1 | station == 2) %>%
    group_by(year, patch, station) %>%
    summarise(x = mean(x),
              y = mean(y))

cameras_stations_spatial <- st_as_sf(cameras_stations, coords = c("x", "y"))
cameras_stations_spatial <- st_set_crs(cameras_stations_spatial, value = proj)

#Other cameras, not at stations.
cameras_no_stations <- cameras %>%
    filter(is.na(station))

cameras_no_stations_spatial <- st_as_sf(cameras_no_stations, coords = c("x", "y"))
cameras_no_stations_spatial <- st_set_crs(cameras_no_stations_spatial, value = proj)
```

Icons symbolizing cameras
```{r}
camera_icon_circle = tmap_icons("data/import/Camera_icon_for_map_circle.png") #class = list
camera_icon = tmap_icons("data/import/Camera_icon_for_map_no_circle.png") #class = list
```

Coordinate for field station
```{r}
#Las Cruces Biological Station
lcbs = data.frame(x = 284524.95, y = 971675.99, label = "Las Cruces Biological Station")
lcbs_spatial = st_as_sf(lcbs, coords = c("x", "y"))
lcbs_spatial <- st_set_crs(lcbs_spatial, value = proj)
```

Boundary of Coto Brus canton
```{r}
coto_brus = read_sf(dsn = "data/import/Cantones_de_Costa_Rica-shp", layer = "5894e940-8455-4376-a1bc-ab05875cd4092020329-1-vyv616.0a2l") %>%
  filter(NOM_CANT_1 == "COTO BRUS")

coto_brus_utm = sf::st_transform(coto_brus, crs = sf::st_crs(proj)) #set projection to forest projection
coto_brus_utm_sp = sf::as_Spatial(coto_brus_utm) #sf to sp
```

Boundaries of countries
```{r}
countries = ne_download(scale = 10,
                       type = "countries",
                       category = "cultural",
                       destdir = tempdir(),
                       load = TRUE,
                       returnclass = "sf")

countries_subset = countries %>%
  filter(NAME == "Costa Rica" | NAME == "Nicaragua" | NAME == "Panama")

st_crs(countries_subset)$proj4string #lat/lon
countries_subset_utm = sf::st_transform(countries_subset, crs = proj)
```

Forest/non-forest layers
```{r, include = FALSE, eval = FALSE}
#My hand-digitized forest/nonforest layer (generally only within 1000m radius of study sites)
forest = raster::raster("data/import/Leimberger_GE_forest_raster_with_matrix_20200630.tif") 
raster::crs(forest) #lat/lon

#Chase Mendenhall's digitization as base map. Doesn't cover entire study area, since mostly clipped to Coto Brus boundary
chase_forest = raster::raster("data/import/Mendenhall_GE_tree_cover_map_hand_digitized.tif")
raster::crs(chase_forest) #lat/lon

#Convert fron lat/long to UTM
projstring <- "+proj=utm +zone=17 +ellps=WGS84 +units=m +no_defs" 
forest = raster::projectRaster(forest, crs = projstring)
chase_forest = raster::projectRaster(chase_forest, crs = projstring)

#Export the UTM raster layers since this step takes a while to run; can just import the UTM versions moving forward
path_name <- c("data/export/for_analysis")
raster::writeRaster(forest, filename = file.path(path_name, "Leimberger_GE_forest_layer_UTM.tif"), overwrite=FALSE)
raster::writeRaster(chase_forest, filename = file.path(path_name, "Mendenhall_GE_forest_layer_UTM.tif"), overwrite=FALSE)
```

```{r}
forest = raster::raster("data/export/for_analysis/Leimberger_GE_forest_layer_UTM.tif") 
chase_forest = raster::raster("data/export/for_analysis/Mendenhall_GE_forest_layer_UTM.tif")
```

## Step 2: Process forest layers

My data: reclassify and clip to 1000m buffer around sites (1000-m buffer = "focal landscape")
```{r}
#Create base table to be filled in. Will consist of each patch and year combination
base_table <- focal_areas %>%
  select(patch, year) %>%
  st_set_geometry(value = NULL) %>% #drop sf geometry column
  left_join(exp_info)

#Buffer all centroids to create focal landscapes
create_landscapes <- function(patch_id, year_id, centroids){
  
  #Select centroids corresponding to PATCH AND YEAR
  
  if(!is.na(year_id)){
    
    centroid <- centroids %>%
      filter(patch == patch_id & year == year_id)
  }
  
  if(is.na(year_id)){
    
    centroid <- centroids %>%
      filter(patch == patch_id)
  }
  
  centroid_buffer <- st_buffer(centroid, dist = 1000)
  
  return(centroid_buffer)
}

#Run function to add buffers

#One landscape per replicate
landscapes <- base_table %>%
  mutate(landscapes = pmap(list(patch, year), ~create_landscapes(patch_id = ..1, year_id = ..2, centroids = centroids_spatial))) %>%
  select(-year, -patch, -replicate) %>% #Remove to avoid duplicate columns
  unnest(col = landscapes)

#class(landscapes$geometry) #geometry is a sfc_POLYGON

#One landscape per focal area (for sites that were re-used, this is mean of all centroids)
mean_landscapes <- base_table %>%
  distinct(patch) %>%
  mutate(landscapes = pmap(list(patch), ~create_landscapes(patch_id = ..1, year_id = NA, centroids = mean_centroids_spatial))) %>%
  select(-patch) %>% #Remove to avoid duplicate columns
  unnest(col = landscapes) %>%
  st_as_sf()

# Reclassify all values 
# https://rdrr.io/cran/raster/man/reclassify.html
rc_matrix <- matrix(c(-Inf, 1, 0, 1, Inf, 1), ncol=3, byrow=TRUE) #If > -Inf and < 1, should be ZERO. If >= 1 and < Inf, should be ONE.
forest_reclass <- raster::reclassify(forest, rc_matrix, include.lowest = TRUE, right = FALSE)

#Crop/mask forest raster to focal landscapes
#Note: these operations seem to cause a large build-up of temp files.
#raster::removeTmpFiles(h=0) #this removes all files. If h = 24, removes all temp files more than 24 hours old, etc.

#For general study area (all 14 sites + 1000m landscapes)
forest_landscapes_CROP <- raster::crop(forest_reclass, sf::as_Spatial(mean_landscapes$geometry)) #All focal landscapes, created using mean focal area centroid
forest_landscapes_MASK <- raster::mask(forest_landscapes_CROP, sf::as_Spatial(mean_landscapes$geometry)) #All focal landscapes, created using mean focal area centroid
```

Get study area boundary
```{r}
#Function to zoom out from bounding box by certain amount. 'layer' is sf object
zoom_out <- function(layer, adjust){
  
  bb = sf::st_bbox(layer)
  
  bb_adjust = sf::st_bbox(c(xmin = bb[[1]] - adjust, xmax = bb[[3]] + adjust, ymin = bb[[2]] - adjust, ymax = bb[[4]] + adjust), crs = proj)
  
  return(bb_adjust)
  
}

#Create bounding boxes for general study area
#Have to loop through each row
extent_study_area <- mean_landscapes %>% 
  mutate(bbox = map(geometry, st_bbox)) %>%
  mutate(bbox_df = map(bbox, ~as.data.frame(as.list(.x)))) %>%
  unnest(bbox_df) %>%
  summarise(xmin = min(xmin),
            xmax = max(xmax),
            ymin = min(ymin),
            ymax = max(ymax))

adjust = 500
bbox_study_area = sf::st_bbox(c(xmin = extent_study_area$xmin - adjust, xmax = extent_study_area$xmax + adjust, ymin = extent_study_area$ymin - adjust, ymax = extent_study_area$ymax + adjust), crs = proj)
```

Chase data: reclassify and clip to Coto Brus boundary
```{r}
chase_forest_reclass <- raster::reclassify(chase_forest, rc_matrix, include.lowest = TRUE, right = FALSE)
chase_forest_CROP <- raster::crop(chase_forest_reclass, raster::extent(bbox_study_area$xmin, bbox_study_area$xmax, bbox_study_area$ymin, bbox_study_area$ymax))
chase_forest_MASK <- raster::mask(chase_forest_CROP, coto_brus_utm_sp) #remove forest outside of canton boundary.
```

## Step 3: Process spatial data for example site

Bounding boxes/extent for example site to be illustrated in figure
```{r}
#Create bounding boxes for example site
example_site = 30
example_year = 2018

#Focal area, specific to a given year
focal_area_example = focal_areas %>%
  filter(patch == example_site & year == example_year) %>%
  pull(geometry)

bbox_focal_area_example = focal_area_example %>% zoom_out(layer = ., adjust = 25)
bbox_focal_area_example
```

Crop/mask forest raster to focal area
```{r}
#Note: these operations seem to cause a large build-up of temp files.
#raster::removeTmpFiles(h=0) #this removes all files. If h = 24, removes all temp files more than 24 hours old, etc.

#For example site (zoomed in map)
#Need to crop first (if just mask, resolution goes down A LOT)
#Order of extent: xmin, xmax, ymin, ymax

#Crop to focal area
forest_focal_area_example_CROP <- raster::crop(forest_landscapes_MASK, raster::extent(bbox_focal_area_example$xmin, bbox_focal_area_example$xmax, bbox_focal_area_example$ymin, bbox_focal_area_example$ymax)) 
```

Subset nets, cameras to example site & year
```{r}
nets_example = nets_spatial %>%
  filter(patch == example_site & year == example_year)

cameras_stations_example = cameras_stations_spatial %>%
    filter(patch == example_site & year == example_year)

cameras_no_stations_example = cameras_no_stations_spatial %>%
    filter(patch == example_site & year == example_year)
```

## Step 3: Make maps

Overall study area
```{r}
study_area_map = 
  
  tm_shape(chase_forest_MASK, bbox = bbox_study_area) +
    tm_raster(style="cat", palette = c('white', 'grey60'), alpha = 1, legend.show = FALSE) +
  
  # tm_shape(coto_brus) +
  #   tm_borders(lwd = 1, col = "black") +

  tm_shape(forest_landscapes_MASK) +
    tm_raster(style = "cat", palette = c('white', 'grey60'), legend.show = FALSE) +
  
  tm_shape(mean_centroids_spatial) +
    tm_symbols(shape = 19, col = "black", size = 0.25) +

  tm_shape(lcbs_spatial) +
    tm_symbols(shape = 4, col = "black", size = 1, border.lwd = 4) +
    tm_text("label", just = "left", xmod = 0.7, ymod = 0.0, size = 1.5) +
    
  tm_compass(type = "arrow", position = c(0.06, 0.1), just = c("center"), size = 2.5, show.labels = 1, text.size = 1.5) + #show.labels value of 1 means only show north
  tm_scale_bar(position = c(0.24, 0.01), just = c("center"), text.size = 1.5, breaks = c(0, 1, 2, 3, 4, 5), bg.color = "white", bg.alpha = 0) +
  tm_layout(inner.margins = c(0,0,0,0), outer.margins=c(0,0,0,0), frame.lwd = 2)
```

Inset map of Costa Rica
```{r}
#Bounding box of box -- NEED TO ADJUST TO ZOOM INTO COSTA RICA MORE
#https://www.jla-data.net/eng/adjusting-bounding-box-of-a-tmap-map/
bbox_countries = st_bbox(countries_subset_utm)

xrange <- bbox_countries$xmax - bbox_countries$xmin # range of x values
yrange <- bbox_countries$ymax - bbox_countries$ymin # range of y values

bbox_countries[1] <- bbox_countries[1] + (0.15 * xrange) # xmin - left
bbox_countries[3] <- bbox_countries[3] - (0.45 * xrange) # xmax - right
bbox_countries[2] <- bbox_countries[2] + (0.25 * yrange) # ymin - bottom
bbox_countries[4] <- bbox_countries[4] - (0.35 * yrange) # ymax - top

#Make inset map of countries
countries_map = 
  
  tm_shape(countries_subset_utm, bbox = bbox_countries) +
    tm_polygons(col = "NAME", palette = c("white", "white", "white"), legend.show = FALSE) + #Order of countries is CR, Nicaragua, Panama. 
  
   tm_shape(countries_subset_utm, bbox = bbox_countries) +
    tm_borders(lwd = 3, col = "black") +
  
    #Labels for countries
    #Origin located at the bottom left, so negative xmod move the text to the left, and negative ymod values to the bottom.
    tm_shape(countries_subset_utm) +
      tm_text("NAME", size = 1.5, col = "black", fontface = c("plain"), just = "center", xmod = c(1.5, 1.5, -14), ymod = c(0, -9, 1)) + #Position of country names depends on export size

    #Las Cruces Biological Station
    tm_shape(lcbs_spatial) +
    tm_symbols(shape = 4, col = "black", size = 4, border.lwd = 10) +

    tm_layout(inner.margins = c(0,0,0,0), outer.margins=c(0,0,0,0), frame.lwd = 4)

countries_map
```

Zoomed-in map of focal area
```{r}
focal_area_map = 
  
  #FOREST CLASSIFICATION
  tm_shape(forest_focal_area_example_CROP, bbox = bbox_focal_area_example, unit = "m") + #Make units m instead of km
    tm_raster(style="cat", palette = c('white', 'grey60'), legend.show = FALSE) +

  #FOCAL AREA (OUTLINED)
  tm_shape(focal_area_example) +
    tm_borders(lwd = 5,  col = "#BA0022") +
  
  #FOCAL AREA (FILLED)
  # tm_shape(focal_area_example) +
  #   tm_polygons(col = "#BA0022", border.col = NULL) +
  
  #MIST NETS
  tm_shape(nets_example) +
    tm_symbols(shape = 24, col = 'black', alpha = 1, size = 0.2,  border.lwd = 1, border.col = "black") +

  #CAMERAS - STATIONS
  tm_shape(cameras_stations_example) +
    tm_symbols(shape = camera_icon_circle, border.col = NULL, size = 0.8, legend.shape.show = FALSE) +

  #CAMERAS - ADDITIONAL LOCATIONS
   tm_shape(cameras_no_stations_example) +
    tm_symbols(shape = camera_icon, border.col = NULL, size = 0.8, legend.shape.show = FALSE) +

  tm_scale_bar(position = c("left", "bottom"), text.size = 1.5, breaks = c(0, 50, 100), bg.color = "white", bg.alpha = 0) + 
  tm_layout(inner.margins = c(0,0,0,0), outer.margins=c(0,0,0,0), frame.lwd = 4)
```

## Step 5: Make legend

Export as png because sizing is super wonky otherwise (auto-adjusts, so don't have much control)

https://github.com/mtennekes/tmap/issues/312
The content of the legend will have some width, based on the content of the legend itself, and on parameters such as legend.text.size. Let me call this the normal legend width.

legend.width is a a threshold value. When the normal legend width is smaller than legend.width, nothing happens, but when it is larger, the content of the legend will be shrunk by decreasing the font sizes and omitting labels if needed.
```{r}
#To add icon and avoid 'Error in shapes[i] - 999: non-numeric argument to binary operator'
#https://gis.stackexchange.com/questions/389361/adding-tmap-icon-to-legend-in-r

all_layers_legend = 
  
  #FOREST CLASSIFICATION
  tm_shape(forest_focal_area_example_CROP, bbox = bbox_focal_area_example, unit = "km") + #Make units m instead of km
    tm_raster(style="cat", palette = c('white', 'grey60'), title = "", legend.show = FALSE) +
    tm_add_legend(title = "", type = "fill", labels = c("Non-forest", "Forest"), col = c('white', 'grey60'), border.lwd = 1, border.col = "black") +
  
  #SITE
  tm_shape(mean_centroids_spatial) +
    tm_symbols(shape = 21, col = 'black', size = 0.25) +
    tm_add_legend(type = 'symbol', labels = 'Site', shape = 21, col = 'black', size = 4, border.col = "white", border.lwd = 25) +
  
  #FOCAL AREA (OUTLINED)
  tm_shape(focal_area_example) +
    tm_borders(lwd = 3,  col = "#BA0022") +
    tm_add_legend(title = "", type = 'line', labels = 'Focal area', lwd = 5, size = 4, col = "#BA0022", legend.format = list(text.align = "left")) +
  
  #MIST NETS
  tm_shape(nets_example) +
    tm_symbols(shape = 24, col = 'black', size = 4) +
    tm_add_legend(title = "", type = 'symbol', labels = 'Mist net', shape = 24, col = 'black', size = 4, border.col = "white", border.lwd = 25) + #Use border line width to create smaller symbol
  
  #CAMERAS - STATIONS
  tm_shape(cameras_stations_example) +
    tm_symbols(shape = camera_icon_circle, border.col = NULL, size = 1, legend.shape.show = FALSE) +
    tm_add_legend(title = "", type = "symbol", labels = "Camera station", shape = list(camera_icon_circle), size = 4, border.col = "white") +

  #CAMERAS - ADDITIONAL LOCATIONS
   tm_shape(cameras_no_stations_example) +
    tm_symbols(shape = camera_icon, border.col = NULL, size = 1, legend.shape.show = FALSE) +
    tm_add_legend(title = "", type = "symbol", labels = "Additional camera", shape = list(camera_icon), size = 4, border.col = "white") +
  
  #Just get legend
  tm_layout(legend.only = TRUE,
            legend.text.size = 3, legend.title.size = 4,
            inner.margins = c(0,0,0,0), outer.margins=c(0,0,0,0))

all_layers_legend
```

## Step 6: Calculate distance between sites within replicate (for Methods/Supplemental methods)

```{r}
#Function to calculate distance between focal landscapes in same replicate
calculate_distance <- function(data, group_id){
  
  #Select landscapes from same group (replicate)
  data_same_group <- data %>%
    filter(replicate == group_id)
  
  distance <- st_distance(data_same_group$geometry, by_element = FALSE)
  return(distance[[2]]) #first element in vector is zero; second element is actual distance. 

}
  
#Calculate distance between sites
distances <- base_table %>%
  mutate(distance = map(replicate, ~calculate_distance(data = centroids_spatial, group_id = .))) %>%
  unnest(distance) %>%
  arrange(replicate)

#These are the distances between SITES. Distance between p203 & p30 cannot be calculated (shows up as zero) because there seems be very slight overlap.
distances_sum <- distances %>%
  distinct(replicate, distance) %>%
  mutate(distance = units::drop_units(distance)) %>% #Remove 'unit' attributes (meters)
  summarise(min = min(distance),
            max = max(distance),
            median = median(distance),
            mean = mean(distance),
            sd = sd(distance))
```

## Step 7: Export maps, legend, and distances between sites

Maps
```{r}
#NEED TO EXPORT WITH ASPECT RATIO OF BOUNDING BOX TO AVOID EXTRA SPACE BEING EXPORTED
ar_study_area <- (bbox_study_area$xmax - bbox_study_area$xmin)/(bbox_study_area$ymax - bbox_study_area$ymin) #width/height
tmap_save(study_area_map, filename = "results/making_maps/Study_area_map.png",
          dpi=300, height=9, width=9*ar_study_area, units="in")

ar_countries <- (bbox_countries$xmax - bbox_countries$xmin)/(bbox_countries$ymax - bbox_countries$ymin) #width/height
tmap_save(countries_map, filename = "results/making_maps/Costa_Rica_map.png",
          dpi=300, height=5, width=5*ar_countries, units="in")

#CRASHES IF TRY TO EXPORT AT 300 DPI AT SIZE LARGER THAN 5x5 :(
ar_focal_area <- (bbox_focal_area_example$xmax - bbox_focal_area_example$xmin)/(bbox_focal_area_example$ymax - bbox_focal_area_example$ymin) #width/height
tmap_save(focal_area_map, filename = "results/making_maps/Focal_area_map_Matching_width.png", dpi=300, height=5/ar_focal_area, width=5, units="in") #Width matches width of other small figures
tmap_save(focal_area_map, filename = "results/making_maps/Focal_area_map_Matching_height.png", dpi=300, height=5, width=5*ar_focal_area, units="in") #Height matches height of other small figures
```

Legend
```{r}
tmap_save(all_layers_legend, filename = "results/making_maps/Legend.png", dpi=300, height=15, width=9, units="in")
```

Distances
```{r}
write.csv(distances, "results/making_maps/Distances_between_paired_sites.csv")
write.csv(distances_sum, "results/making_maps/Distances_between_paired_sites_sum.csv")
```

