---
title: "Analyzing camera data"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

**Goals**

Analyze how experimental *Heliconia* removal influences:

- Visitation rates to focal *Heliconia* plants (those that remained uncovered throughout the experiment)
  * Visitation from all hummingbirds
  * Visitation from individual color-marked hummingbirds (2017-2018 only)

- Visitation rates to non-*Heliconia* plants
  * Visitation from all hummingbirds
  * Visitation from individual color-marked hummingbirds (2017-2018 only)

For each analysis, I will examine (A) all hummingbird species, and (B) species that are *Heliconia* specialists (green hermits and violet sabrewings).

```{r setup, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)

#Packages for statistical modeling
library(glmmTMB)
library(AICcmodavg)
library(DHARMa)
library(emmeans)
library(ggeffects)

#Packages for data wrangling
library(dplyr)
library(tidyr)
library(lubridate)
library(purrr)

#Packages for plotting
library(ggplot2)
library(ggrepel)
library(ggpubr)

#Set up parallel processing (likelihood profile CI take forever to run!)
library(future)
plan(multisession)

#Set seed
set.seed(1)
```

## Step 1: Import data and functions, prepare for analysis

**Get data**
```{r}
#Camera data, visits summarized across birds
visit_data <- read.csv("../../data/export/for_analysis/Camera_visitation_rates.csv") %>%
  mutate(analysis = ifelse(plant_species == "HETO", "camera_HETO", "camera_non-HETO")) %>%
  mutate(subanalysis = "all_birds")

#Camera data, visits by individual birds
#Decided not to exclude birds that have no visits during the pre period (determined for HETO and non-HETO separately)
visit_data_marked <- read.csv("../../data/export/for_analysis/Camera_visitation_rates_marked_birds.csv") %>%
  mutate(analysis = ifelse(plant_species == "HETO", "camera_HETO", "camera_non-HETO")) %>%
  mutate(subanalysis = "marked_birds")

#Resource data. Need to add quantitative treatment measure here (*Heliconia* calories removed/ha)
heto_removed <- read.csv("../../data/export/for_analysis/Site_and_replicate_characteristics.csv") %>%
  select(year, patch, control_treatment, calories_removed_per_ha)

#Plant names
plant_species_names <- read.csv("../../data/import/data/Plant_codes_species_list.csv") %>%
  select(plant_family, plant_scientific_name, plant_species)
```

**How many non-Heliconia species had camera data pre and post? Did all species have sightings?**
```{r}
#Calculate total number of species in data (and total # with sightings)
nonheto_data <- visit_data %>%
  filter(analysis == "camera_non-HETO" & subanalysis == "all_birds" & bird_group == "all_spp")

nonheto_species <- nonheto_data %>%
  group_by(plant_species) %>%
  summarise(num_sightings = sum(sightings)) %>%
  arrange(num_sightings) %>%
  ungroup()

nonheto_species_with_sightings <- nonheto_species %>%
  filter(num_sightings > 0)

#Which plant species have the most data? In terms of replicates (actual number of rows will be double this, because have data pre and post)
nonheto_species_sample_size <- nonheto_data %>%
  distinct(year, patch, plant_species) %>%
  group_by(plant_species) %>%
  summarise(num_replicates = n()) %>%
  arrange(desc(num_replicates)) %>%
  left_join(plant_species_names) %>%
  left_join(nonheto_species) %>%
  select(plant_family, plant_scientific_name, plant_species, num_replicates, num_sightings) %>%
  filter(num_sightings > 0)

#Export list for Supp info
write.csv(nonheto_species_sample_size, "../../data/export/supp_tables/List_of_non-Heliconia_camera_species.csv")
```

**Prepare data for analysis**
```{r}
#1. Combine data
#2. Remove plant species that had no sightings from any hummingbird species, pre or post
#3. Log-transform HETO calories removed
#4. Remove plants without flower counts (GINGY and MARA-VER)
visit_data_for_analysis <- visit_data_marked %>%
  bind_rows(visit_data) %>%
  left_join(heto_removed) %>% 
  filter(plant_species == "HETO" | plant_species %in% nonheto_species_with_sightings$plant_species) %>%
  mutate(exp_phase = factor(exp_phase, levels = c("pre", "post"))) %>%
  mutate(control_treatment = factor(control_treatment, levels = c("control", "treatment"))) %>%
  mutate(year_patch = paste(year, patch, sep = "_")) %>%
  mutate(log_calories_removed_per_ha = log(calories_removed_per_ha + 1)) %>%
  filter(!is.na(flowers) & flowers != "NA") %>%
  select(analysis, subanalysis, bird_group, everything())

#Check: how many plant species, including HETO? All birds dataset
visit_data_for_analysis %>% filter(subanalysis == "all_birds") %>% pull(plant_species) %>% unique() %>% length()

#Check: how many plant species, including HETO? Marked birds dataset
visit_data_for_analysis %>% filter(subanalysis == "marked_birds") %>% pull(plant_species) %>% unique() %>% length()
```

**Import functions**
```{r step1a}
source("../../code/helper_functions/Modeling_helper_functions.R")
source("../../code/helper_functions/Plotting_helper_functions.R")
source("../../code/helper_functions/Extract_data_from_safely_and_quietly_lists.R")
```

## Step 2: Create datasets for each analysis 

**Get organized**
```{r create_table_to_hold_results}
#Create tables that will be filled in with models and model results
analysis = c("camera_HETO", "camera_non-HETO")
subanalysis = c("all_birds", "marked_birds")
bird_group = c("all_spp", "greh_visa")
plant_species = nonheto_species_sample_size %>% filter(num_replicates > 10) %>% pull(plant_species)
model_type = c("categorical", "quantitative")
model_name = c("control/treatment * pre/post", "calories removed/ha * pre/post")
treatment_variable = c("control_treatment", "log_calories_removed_per_ha")
model_types_names = data.frame(model_type = model_type, model_name = model_name, treatment_variable = treatment_variable)

#Models for HETO visitation and non-HETO visitation (combined across all species)
heto_nonheto_combined_base_table <- crossing(analysis, subanalysis, bird_group, model_type)

#Models for non-HETO visitation (plant species analyzed separately)
#If want to look at GREH/VISA as well, can cross with 'bird_group". But doing this causes convergence problems for plant species with little to no visitation from these hummingbirds (RABO, MARA)
nonheto_separate_base_table <- data.frame(analysis = "camera_non-HETO_separate", subanalysis = "all_birds", plant_species = plant_species, model_type = "categorical", bird_group = "all_spp")

#Combine
base_table <- heto_nonheto_combined_base_table %>%
  bind_rows(nonheto_separate_base_table) %>%
  left_join(model_types_names) %>%
  mutate(yvar = "sightings") %>%
  arrange(analysis, subanalysis, model_type, plant_species, bird_group) %>%
  mutate(model_number = 1:length(yvar)) %>%
  mutate(title = paste(analysis, subanalysis, bird_group, sep = "_")) %>%
  mutate(title = ifelse(analysis == "camera_non-HETO_separate", paste(analysis, subanalysis, plant_species), title)) %>%
  mutate(subtitle = yvar) %>%
  select(model_number, analysis, yvar, subanalysis, everything())
```

**Filter master dataset to relevant sub-dataset & scale continuous predictors**
```{r}
subset_data <- function(dataset, analysis, subanalysis, bird_group, plant_species){
  
  if(analysis != "camera_non-HETO_separate"){
    
    dataset <- dataset %>%
      filter(analysis == {{ analysis }}) %>%
      filter(subanalysis == {{ subanalysis}}) %>%
      filter(bird_group == {{ bird_group }})
    
  }
  
  if(analysis == "camera_non-HETO_separate"){
    
    dataset <- dataset %>%
      filter(analysis == "camera_non-HETO") %>%
      filter(subanalysis == {{ subanalysis}}) %>%
      filter(bird_group == {{ bird_group }}) %>%
      filter(plant_species == {{ plant_species }})
  }
  
  #Scale continuous predictors
  dataset <- dataset %>%
    mutate(across(c(log_calories_removed_per_ha, flowers), ~c(scale(.))))

  return(dataset)
  
}

#Create datasets (will add models in later step)
data <- base_table %>%
    mutate(data = pmap(list(analysis, subanalysis, bird_group, plant_species), ~subset_data(dataset = visit_data_for_analysis, analysis = ..1, subanalysis = ..2, bird_group = ..3, plant_species = ..4)))
```

## Step 3: Initial model fitting

For count data, there multiple possible distributions. I need to choose between Poisson and negative binomial (nbinom1 and nbinom2) and also see if there is support for zero-inflation or not. Will check assumptions for all models again later on.

**Heliconia visitation rate: all birds, including unmarked birds**
```{r, include = FALSE, eval = FALSE}
fit_data01 <- data %>%
  filter(analysis == "camera_HETO" & subanalysis == "all_birds" & bird_group == "all_spp" & model_type == "categorical") %>%
  pull(data) %>%
  as.data.frame()

m1 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch), data = fit_data01, na.action = na.omit, family = "poisson", ziformula = ~0)

m2 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch), data = fit_data01, na.action = na.omit, family = "poisson", ziformula = ~1)

m3 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch), data = fit_data01, na.action = na.omit, family = "nbinom1", ziformula = ~0)

m4 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch), data = fit_data01, na.action = na.omit, family = "nbinom1", ziformula = ~1)

m5 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch), data = fit_data01, na.action = na.omit, family = "nbinom2", ziformula = ~0)

m6 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch), data = fit_data01, na.action = na.omit, family = "nbinom2", ziformula = ~1)

#Combine models
model_fitting01 <- tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6"), model = list(m1, m2, m3, m4, m5, m6)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting01 %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Check to make sure assumptions look OK
model_fitting01$dharma_plot[[3]]
model_fitting01$dharma_overdisp_plot[[3]]
model_fitting01$dharma_zeroinfl_plot[[3]]
```

**Non-Heliconia visitation rate (all plant species together): all birds, including unmarked birds**
```{r, include = FALSE, eval = FALSE}
fit_data02 <- data %>%
  filter(analysis == "camera_non-HETO" & subanalysis == "all_birds" & bird_group == "all_spp" & model_type == "categorical") %>%
  pull(data) %>%
  as.data.frame()

m1 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species), data = fit_data02, na.action = na.omit, family = "poisson", ziformula = ~0)

m2 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species), data = fit_data02, na.action = na.omit, family = "poisson", ziformula = ~1)

m3 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species), data = fit_data02, na.action = na.omit, family = "nbinom1", ziformula = ~0)

m4 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species), data = fit_data02, na.action = na.omit, family = "nbinom1", ziformula = ~1)

m5 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species), data = fit_data02, na.action = na.omit, family = "nbinom2", ziformula = ~0)

m6 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species), data = fit_data02, na.action = na.omit, family = "nbinom2", ziformula = ~1)

#Combine models
model_fitting02 <- tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6"), model = list(m1, m2, m3, m4, m5, m6)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting02 %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Check to make sure assumptions look OK
model_fitting02$dharma_plot[[3]]
model_fitting02$dharma_overdisp_plot[[3]]
model_fitting02$dharma_zeroinfl_plot[[3]]

#model 4 (ZI model) is technically best in terms of AIC, but does not converge for GREH/VISA; using second-best model (model 3) instead, because assumptions look fine and it converges for GREH/VISA (and is the best model for that group in terms of AIC)
```

**Non-Heliconia visitation rate (plant species separate): all birds, including unmarked birds**
```{r, include = FALSE, eval = FALSE}
#Function to automate model fitting for separate non-Heliconia plant species
fit_model <- function(dataset){
  
  #Don't have enough data to model zero-inflation without errors/convergence issues so will not include ZI-models here
  m1 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch), data = dataset, na.action = na.omit, family = "poisson", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

  m3 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch), data = dataset, na.action = na.omit, family = "nbinom1", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
                        
  m5 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch), data = dataset, na.action = na.omit, family = "nbinom2", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
                        
  #Combine models
  model_fitting <- tibble(model_name = c("m1", "m3", "m5"), model = list(m1, m3, m5)) %>%
    mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
    mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
           dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
           dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
    mutate(AICc = map(model, MuMIn::AICc))

  return(model_fitting)

}

#Testing to see which models have errors/convergence issues
# fit_model_safely <- safely(.f = fit_model) #To run without getting errors
# (test01 <- fit_model_safely(dataset = data, plant_species = "MARA"))
# (test02 <- fit_model_safely(dataset = data, plant_species = "PAV-ROJ-AMA"))
# (test03 <- fit_model_safely(dataset = data, plant_species = "CEPO"))
# (test04 <- fit_model_safely(dataset = data, plant_species = "TUBO-AMA"))
# (test05 <- fit_model_safely(dataset = data, plant_species = "HAPA"))
# (test06 <- fit_model_safely(dataset = data, plant_species = "PALU"))
# (test07 <- fit_model_safely(dataset = data, plant_species = "RABO"))
# (test08 <- fit_model_safely(dataset = data, plant_species = "BOCA-ROJA"))
# (test09 <- fit_model_safely(dataset = data, plant_species = "COSTBAR"))

#Initial model fitting for separate non-Heliconia plant species
#Only look at species with more than 10 replicates/20 rows 
model_fitting_nonheto_separate <- nonheto_species_sample_size %>%
  filter(num_replicates > 10) %>%
  arrange(plant_species) %>%
  left_join(data) %>%
  mutate(fit_with_info = map(data, ~fit_model(dataset = .)))

#Extract AICc ranks
AICc_ranks <- model_fitting_nonheto_separate %>%
  select(plant_species, num_replicates, fit_with_info) %>%
  unnest(fit_with_info) %>%
  select(plant_species, num_replicates, model_name, AICc)

#Top AICc models
AICc_best_models <- AICc_ranks %>%
  group_by(plant_species, num_replicates) %>%
  slice(which.min(AICc)) %>%
  arrange(desc(num_replicates))

#According to AICc, model 3 is best for all except for:
#BOCA-ROJA: model 5 - but AICc is basically the same as other models (<1)
#CEPO: model 1
#COSTBAR: model 1

#But do best models according to AICc meet assumptions? Check to make sure assumptions look OK. I've noted best model(s) according to assumptions below.
model_fitting_nonheto_separate %>% filter(plant_species == "BOCA-ROJA") %>% select(-model_name) %>% unnest(fit_with_info) %>% pull(dharma_plot) #m1
model_fitting_nonheto_separate %>% filter(plant_species == "CEPO") %>% select(-model_name) %>% unnest(fit_with_info) %>% pull(dharma_plot) #m5
model_fitting_nonheto_separate %>% filter(plant_species == "COSTBAR") %>% select(-model_name) %>% unnest(fit_with_info) %>% pull(dharma_plot) #m3
model_fitting_nonheto_separate %>% filter(plant_species == "HAPA") %>% select(-model_name) %>% unnest(fit_with_info) %>% pull(dharma_plot) #m1, m5 (m5 lower AIC)
model_fitting_nonheto_separate %>% filter(plant_species == "MARA") %>% select(-model_name) %>% unnest(fit_with_info) %>% pull(dharma_plot) #m1, m3 (m3 lower AIC)
model_fitting_nonheto_separate %>% filter(plant_species == "PALU") %>% select(-model_name) %>% unnest(fit_with_info) %>% pull(dharma_plot) #m3 
model_fitting_nonheto_separate %>% filter(plant_species == "PAV-ROJ-AMA") %>% select(-model_name) %>% unnest(fit_with_info) %>% pull(dharma_plot) #any (m3 lower AIC)
model_fitting_nonheto_separate %>% filter(plant_species == "RABO") %>% select(-model_name) %>% unnest(fit_with_info) %>% pull(dharma_plot) #m3 but still rather squiggly :(
model_fitting_nonheto_separate %>% filter(plant_species == "TUBO-AMA") %>% select(-model_name) %>% unnest(fit_with_info) %>% pull(dharma_plot) #m3, m5 (m3 lower AIC)

#Troubleshooting RABO models...
rabo_data <- visit_data_for_analysis %>% filter(plant_species == "RABO" & subanalysis == "all_birds" & bird_group == "all_spp") #This dataset does not have any scaled variables so can experiment with hours as covariate (not offset) more easily

rabo_fit_zip <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + scale(flowers) + offset(log(hours)) + (1|patch/year_patch), data = rabo_data, na.action = na.omit, family = "poisson", ziformula = ~1, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

rabo_fit_genpois <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + scale(flowers) + offset(log(hours)) + (1|patch/year_patch), data = rabo_data, na.action = na.omit, family = "genpois", ziformula = ~0)

rabo_fit_log_flowers <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + scale(log(flowers)) + offset(log(hours)) + (1|patch/year_patch), data = rabo_data, na.action = na.omit, family = "nbinom1", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

rabo_fit_log_flowers_no_offset <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + scale(log(flowers)) + scale(hours) + (1|patch/year_patch), data = rabo_data, na.action = na.omit, family = "nbinom1", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

rabo_fit_flowers2 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + I(scale(flowers)^2) + offset(log(hours)) + (1|patch/year_patch), data = rabo_data, na.action = na.omit, family = "nbinom1", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

rabo_fit_flowers2_no_offset <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + I(scale(flowers)^2) + scale(hours) + (1|patch/year_patch), data = rabo_data, na.action = na.omit, family = "nbinom1", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

simulateResiduals(rabo_fit_zip) %>% plot()
simulateResiduals(rabo_fit_genpois) %>% plot()
simulateResiduals(rabo_fit_log_flowers) %>% plot()
simulateResiduals(rabo_fit_log_flowers_no_offset) %>% plot()
simulateResiduals(rabo_fit_flowers2) %>% plot()
simulateResiduals(rabo_fit_flowers2_no_offset) %>% plot()

map(list(rabo_fit_zip, rabo_fit_genpois, rabo_fit_log_flowers, rabo_fit_log_flowers_no_offset, rabo_fit_flowers2, rabo_fit_flowers2_no_offset), MuMIn::AICc)

#DECISIONS:
#Model 1 (Poisson) for BOCA-ROJA
#Model 3 (nbinom1) for MARA, PALU, PAV-ROJ-AMA, TUBO-AMA, COSTBAR
#Model 3 (nbinom1) for RABO, but with (A) squared term for flowers, and (B) hours as covariate rather than an offset
#Model 5 (nbinom2) for CEPO, HAPA
```

**Heliconia visitation rate: marked birds only**
```{r, include = FALSE, eval = FALSE}
fit_data03 <- data %>%
  filter(analysis == "camera_HETO" & subanalysis == "marked_birds" & bird_group == "all_spp" & model_type == "categorical") %>%
  pull(data) %>%
  as.data.frame()

m1 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/color_id), data = fit_data03, na.action = na.omit, family = "poisson", ziformula = ~0)

m2 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/color_id), data = fit_data03, na.action = na.omit, family = "poisson", ziformula = ~1)

m3 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/color_id), data = fit_data03, na.action = na.omit, family = "nbinom1", ziformula = ~0)

m4 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/color_id), data = fit_data03, na.action = na.omit, family = "nbinom1", ziformula = ~1)

m5 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/color_id), data = fit_data03, na.action = na.omit, family = "nbinom2", ziformula = ~0)

m6 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/color_id), data = fit_data03, na.action = na.omit, family = "nbinom2", ziformula = ~1)

#Combine models
model_fitting03 <- tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6"), model = list(m1, m2, m3, m4, m5, m6)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting03 %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Check to make sure assumptions look OK
model_fitting03$dharma_plot[[1]]
model_fitting03$dharma_overdisp_plot[[1]]
```

**Non-Heliconia visitation rate: marked birds only**
```{r, include = FALSE, eval = FALSE}
fit_data04 <- data %>%
  filter(analysis == "camera_non-HETO" & subanalysis == "marked_birds" & bird_group == "all_spp" & model_type == "categorical") %>%
  pull(data) %>%
  as.data.frame()

m1 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species) + (1|color_id), data = fit_data04, na.action = na.omit, family = "poisson", ziformula = ~0)

m2 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species) + (1|color_id), data = fit_data04, na.action = na.omit, family = "poisson", ziformula = ~1)

m3 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species) + (1|color_id), data = fit_data04, na.action = na.omit, family = "nbinom1", ziformula = ~0)

m4 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species) + (1|color_id), data = fit_data04, na.action = na.omit, family = "nbinom1", ziformula = ~1)

m5 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species) + (1|color_id), data = fit_data04, na.action = na.omit, family = "nbinom2", ziformula = ~0)

m6 <- glmmTMB::glmmTMB(sightings ~ control_treatment * exp_phase + flowers + offset(log(hours)) + (1|patch/year_patch/plant_species) + (1|color_id), data = fit_data04, na.action = na.omit, family = "nbinom2", ziformula = ~1)

#Combine models
model_fitting04 <- tibble(model_name = c("m1", "m2", "m3", "m4", "m5", "m6"), model = list(m1, m2, m3, m4, m5, m6)) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "basic")),
         dharma_zeroinfl_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, model_name), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2,  plot_type = "overdispersion"))) %>%
  mutate(AICc = map(model, MuMIn::AICc))

#Which model is best according to AIC?
model_fitting04 %>%
  select(model_name, AICc) %>%
  unnest(AICc) %>%
  arrange(AICc)

#Check to make sure assumptions look OK
model_fitting04$dharma_plot[[5]]
model_fitting04$dharma_overdisp_plot[[5]]
```

## Step 4: Create models
```{r}
#Function to make model for given analysis
#Alternative optimizer (default is nlminb)
#control = glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS"))
create_model <- function(dataset, analysis, subanalysis, treatment_variable, plant_species){

  #All models will have this part, but will adjust random effects for each model
  base_formula <- paste0("sightings ~ ", treatment_variable, " * exp_phase + flowers + offset(log(hours))")
  
  #Make models for each analysis
  if(analysis == "camera_HETO"){
    
    if(subanalysis == "all_birds"){
      
      model <- glmmTMB(as.formula(paste0(base_formula, " + (1|patch/year_patch)")), data = dataset, na.action = na.omit, family = "nbinom1", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
      
    }
    
    if(subanalysis == "marked_birds"){
      
       model <- glmmTMB(as.formula(paste0(base_formula, " + (1|patch/year_patch/color_id)")), data = dataset, na.action = na.omit, family = "poisson", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
       
    }
    
  }
  
  if(analysis == "camera_non-HETO"){
    
    if(subanalysis == "all_birds"){
      
      model <- glmmTMB(as.formula(paste0(base_formula, " + (1|patch/year_patch/plant_species)")), data = dataset, na.action = na.omit, family = "nbinom1", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
                       
      
    }
    
    if(subanalysis == "marked_birds"){
      
       model <- glmmTMB(as.formula(paste0(base_formula, " + (1|patch/year_patch/plant_species) + (1|color_id)")), data = dataset, na.action = na.omit, family = "nbinom2", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
                        
    }
    
  }
  
  #DECISION: Model 1 (Poisson) for BOCA-ROJA, COSTBAR. Model 5 (nbinom2) for CEPO, HAPA. Model 3 (nbinom1) for MARA and the rest.
  if(analysis == "camera_non-HETO_separate"){
    
    if(plant_species == "BOCA-ROJA"){
      
      model <- glmmTMB(as.formula(paste0(base_formula, " + (1|patch/year_patch)")), data = dataset, na.action = na.omit, family = "poisson", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))
      
    }
    
    nbinom1_species <- c("MARA", "PALU", "PAV-ROJ-AMA", "TUBO-AMA", "COSTBAR")
    if(plant_species %in% nbinom1_species){
      
      model <- glmmTMB(as.formula(paste0(base_formula, " + (1|patch/year_patch)")), data = dataset, na.action = na.omit, family = "nbinom1", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

    }
    
    if(plant_species == "CEPO" | plant_species == "HAPA"){
      
      model <- glmmTMB(as.formula(paste0(base_formula, " + (1|patch/year_patch)")), data = dataset, na.action = na.omit, family = "nbinom2", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

    }
    
    #Model for RABO is tricky...only meets assumptions with the following modifications (squared term for flowers and no offset for hours)
    if(plant_species == "RABO"){
      
      dataset <- dataset %>%
        mutate(across(c(hours), ~c(scale(.)))) #Need to standardize hours here because wasn't scaled in function earlier
      
      model <- glmmTMB(as.formula("sightings ~ control_treatment * exp_phase + I(flowers^2) + hours + (1|patch/year_patch)"), data = dataset, na.action = na.omit, family = "nbinom1", ziformula = ~0, control=glmmTMBControl(optimizer=optim, optArgs=list(method="BFGS")))

    }
    
  }
  
  return(model)
  
}

#Testing function
test01 <- create_model(dataset = data[[12]][[1]], analysis = "camera_HETO", subanalysis = "all_birds", treatment_variable = "control_treatment", plant_species = NA)
test02 <- create_model(dataset = data[[12]][[20]], analysis = "camera_non-HETO_separate", subanalysis = "all_birds", treatment_variable = "control_treatment", plant_species = "RABO")
summary(test01)
summary(test02)

#Create models
models <- data %>%
   mutate(model_quietly = pmap(list(data, analysis, subanalysis, treatment_variable, plant_species), quietly(function(a, b, c, d, e){model <- create_model(dataset = a, analysis = b, subanalysis = c, treatment_variable = d, plant_species = e)})),
          model = map(model_quietly, get_result),
          warning = map(model_quietly, get_warning), 
          convergence = map(model, check_convergence)) %>%
  mutate(xvar_table = map(model, ~data.frame(xvar = all.vars(terms(.))[-1]))) #hours is technically an offset, not a covariate, in most models; could remove entirely by adding [-4] after [-1]

#Make sure there weren't any problems + check to make sure table of predictor variables is correct
models$warning
models$convergence
models$xvar_table #hours is technically an offset, not a covariate, in most models (can ignore)
```

## Step 5: Check assumptions
```{r, fig.show = 'hide', results = 'hide', eval = FALSE}
assumption_checks <- models %>%
  mutate(re_plot = pmap(list(model, title, subtitle), ~check_re(model = ..1, plot_title = ..2, plot_subtitle = ..3))) %>%
  mutate(dharma_object = map(model, ~simulateResiduals(fittedModel = ., n = 1000, plot = FALSE, re.form = ~0))) %>%
  mutate(dharma_plot_safely = pmap(list(dharma_object, title, subtitle),
                                   safely(function(a, b, c){make_dharma_plot(dharma_object = a, plot_title = b, plot_subtitle = c, plot_type = "basic")})),
         dharma_plot = map(dharma_plot_safely, get_result),
         dharma_plot_error = map(dharma_plot_safely, get_error)) %>%
  mutate(dharma_xvar_plot_safely = pmap(list(xvar_table, data, dharma_object, title, subtitle),
                                        safely(function(a, b, c, d, e){make_dharma_xvar_plot(predictor_table = a, dataset = b, dharma_object = c, plot_title = d, plot_subtitle = e)})),
         dharma_xvar_plot = map(dharma_xvar_plot_safely, get_result),
         dharma_xvar_plot_error = map(dharma_xvar_plot_safely, get_error)) %>%
  mutate(dharma_zeroinfl_plot = pmap(list(dharma_object, title, subtitle), ~make_dharma_plot(dharma_object = ..1, plot_title = ..2, plot_subtitle = ..3, plot_type = "zeroinflation")),
         dharma_overdisp_plot = pmap(list(dharma_object, title, subtitle),  ~make_dharma_plot(dharma_object = ..1, plot_title = ..2, plot_subtitle = ..3, plot_type = "overdispersion"))) %>%
  mutate(plotname1 = paste("re_diagnostics_", model_number, ".png", sep = "")) %>%
  mutate(plotname2 = paste("dharma_overall_diagnostics_", model_number, ".png", sep = "")) %>%
  mutate(plotname3 = paste("dharma_xvar_diagnostics_", model_number, ".png", sep = "")) %>%
  mutate(plotname4 = paste("dharma_zeroinfl_diagnostics_", model_number, ".png", sep = "")) %>%
  mutate(plotname5 = paste("dharma_overdisp_diagnostics_", model_number, ".png", sep = ""))

#Export diagnostic plots because they load very slowly in RStudio
path_name <- c("../../results/analysis/assumption_checks/cameras")
walk2(assumption_checks$plotname1, assumption_checks$re_plot, ~ggsave(filename = .x, plot = .y, path = path_name, height = 11.5, width = 15, units = "in", bg = "white"))
walk2(assumption_checks$plotname2, assumption_checks$dharma_plot, ~ggsave(filename = .x, plot = .y, path = path_name, height = 11.5, width = 15, units = "in"))
walk2(assumption_checks$plotname3, assumption_checks$dharma_xvar_plot, ~ggsave(filename = .x, plot = .y, path = path_name, height = 11.5, width = 15, units = "in", bg = "white"))
walk2(assumption_checks$plotname4, assumption_checks$dharma_zeroinfl_plot, ~ggsave(filename = .x, plot = .y, path = path_name, height = 11.5, width = 15, units = "in"))
walk2(assumption_checks$plotname5, assumption_checks$dharma_overdisp_plot, ~ggsave(filename = .x, plot = .y, path = path_name, height = 11.5, width = 15, units = "in"))

#Check for highly influential replicates
#Make plots of DFBETAS and Cook's distance
influence_checks <- models %>%
  mutate(influence_plot = pmap(list(model, data, title, subtitle), ~make_influence_plot(model = ..1, dataset = ..2, plot_title = ..3, plot_subtitle = ..4, group_id = "year_patch"))) %>%
  mutate(plotname6 = paste("influence_diagnostics_", model_number, ".png", sep = ""))

#Export plots
walk2(influence_checks$plotname6, influence_checks$influence_plot, ~ggsave(filename = .x, plot = .y, path = path_name, height = 11.5, width = 15, units = "in", bg = "white"))

#Replicate 2016_58 seems to be pretty influential in non-HETO models for GREH/VISA, perhaps because of GIN-ROS-AMA (highest # sightings in entire dataset). But it's influential in the direction of rewiring, and we're still not finding a statistically significant treatment effect (interaction term).
```

## Step 6: Create results for export
```{r}
#Will also add information about sample size: total # of observations (rows), number of levels per random effect, and the number of replicates (split into 'control' vs. 'treatment')
results <- models %>%
  mutate(summary = map(model, summary),
         summary_tidy = map(model, broom.mixed::tidy),
         confint_wald = map(model, ~calculate_ci(., method_name = "wald"))) %>%
  mutate(num_obs = map(model, get_number_obs),
         num_levels = map(model, get_number_re_levels),
         num_reps = map(data, ~get_sample_size(data = ., vars = c("year", "patch", "control_treatment"), grouping_var = "control_treatment")))
```

## Step 7: Export results as rds file
```{r}
saveRDS(results, "../../results/analysis/rds_files/Camera_results.rds")
```

*WILL EXTRACT RESULTS, CALCULATE CONTRASTS, MAKE PLOTS, ETC. FROM RDS FILES LATER ON IN SINGLE SCRIPT*