---
title: "Comparing site characteristics in control versus treatment replicates"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

**Goal**

Check to see if there are any differences in site characteristics between control and treatment replicates.

**Site characteristics considered**

- Elevation
- Focal area size (ha)
- *Heliconia* density (calories/ha)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(tidyr)
library(purrr)
library(ggplot2)
```

## Step 1: Get data

These data have been combined in a previous script.
```{r}
site_characteristics <- read.csv("../../data/export/for_analysis/Site_and_replicate_characteristics.csv") %>%
  mutate(focal_area_size = ifelse(year == "2016" & control_treatment == "control", NA, focal_area_size)) %>% #these are just filled in from later years because resource surveys not conducted in 2016
  mutate(log_heto_calories_per_ha = log(heto_calories_per_ha)) %>%
  mutate(control_treatment = factor(control_treatment, levels = c("control", "treatment"), labels = c("Control", "Treatment"))) %>%
  unite(col = "year_patch", year, patch, sep = "_", remove = FALSE)
```

Note: Focal area size and *Heliconia* density are unavailable for 2016 control replicates, because resource surveys were not conducted in these years.

## Step 2: Visualize data
```{r}
#Recommended figure widths from journal (pixels @ 300 dpi)
column1x <- 945 #single-column
column1.5x <- 1476 #1.5 columns
column2x <- 1961 #double column

#Sizes for plot elements
size = 9
label_size = size
title_size = size * 1.15
shape_size = 1
line_width = 0.25

path_name <- c("../../results/analysis/figures")
colors <- c("#0E0D37", "#BA0022")
```

```{r}
make_plot = function(dataset, yvar, ylabel, text_size, point_size, line_size){
  
  plot <- 
    
    ggplot(data = dataset, aes_string(x = "control_treatment", y = yvar)) +
  
    #Boxplots in different position than points
    geom_boxplot(aes(fill = control_treatment), colour = "black", width = 0.15, position = position_nudge(x = c(-0.15, 0.15)), alpha = 0.5, outlier.shape = NA, linewidth = line_size) +
    stat_summary(fun = mean, position = position_nudge(x = c(-0.15, 0.15)), geom = "point", shape = 23, size = shape_size, colour = "black", fill = "black") +
    geom_point(aes(fill = control_treatment), colour = "black", shape = 21, position = position_dodge(width = 0.45), alpha = 1, size = shape_size, stroke = line_size) +
    theme_bw(base_size = text_size) +
    scale_fill_manual(values = colors) +
    scale_color_manual(values = colors) +
    theme_bw(base_size = size) +
    theme(legend.position = "none",
          legend.direction = "horizontal",
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.background = element_blank(),
          panel.border = element_rect(colour = "black", fill = NA))+
    labs(x = "", y = ylabel, fill = "", colour = "")
    
  return(plot)
    
} 

(elevation_plot <- make_plot(dataset = site_characteristics, yvar = "elevation", ylabel = "Elevation (m)", text_size = size, point_size = shape_size, line_size = line_width))
(focal_area_plot <- make_plot(dataset = site_characteristics, yvar = "focal_area_size", ylabel = "Focal area size (ha)", text_size = size, point_size = shape_size, line_size = line_width))
(heto_density_plot <- make_plot(dataset = site_characteristics, yvar = "log_heto_calories_per_ha", ylabel = expression("Ln"~italic(Heliconia)~"calories/ha"), text_size = size, point_size = shape_size , line_size = line_width))

site_characteristic_multiplot <- ggpubr::ggarrange(elevation_plot, focal_area_plot, heto_density_plot, nrow = 1, ncol = 3, labels = c("(a)", "(b)", "(c)"), font.label = list(size = label_size, face = "plain"))

# ggview::ggview(site_characteristic_multiplot, width = column2x, height = column2x/3, units = "px")
ggsave(file.path(path_name, "FigS1_Site_characteristics.png"), site_characteristic_multiplot, dpi = 300, width = column2x, height = column2x/3, units = "px", bg = "white", device = "tiff")
```

## Step 3: Test whether there are any statistical differences in site characteristics (control vs. treatment replicates)
```{r}
t.test(elevation ~ control_treatment, data = site_characteristics)
t.test(focal_area_size ~ control_treatment, data = site_characteristics, var.equal = FALSE)
t.test(log_heto_calories_per_ha ~ control_treatment, data = site_characteristics, var.equal = FALSE)
```