---
title: "Summarizing nectar measurements (for resource estimation)"
output: html_document
knit: (function(inputFile, encoding) {
      out_dir <- "knitted_markdown_files";
      rmarkdown::render(inputFile,
                        encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(readxl)
library(tidyr)
library(dplyr)
library(ggplot2)
```

**Overall goal**

Estimate resource availability per site and year, in terms of calories available to hummingbirds.

**Goal of this code**

Summarize nectar volume and concentration from the nectar measurements collected in the field. Nectar measurements are a combination of those from 2018 (Leimberger PhD project) and those from 2014 (Birkett undergrad thesis project.) By summarizing average nectar volume and concentration per species, I can calculate the number of calories per flower (in a later step).


## Step 1: Import data and functions

Import helper functions
```{r step1a}
source("../../code/helper_functions/Calculate_basic_summary_stats.R")
```

Get nectar measurements
```{r step1b}
path_name <- c("../../data/import/misc_data_for_resource_estimate")

#Nectar measurements from field
nectar <- read.csv(file.path(path_name, "CR_Nectar_Data_20210914.csv"))
```

## Step 2: Summarize nectar volume (microliters) and concentration (%w/w) by plant species

Data **included** in this summary

- Potted plants
- Robbed flowers

Data **excluded** in this summary

- "Old" flowers (Birkett data only)
- Unbagged flowers

Filter data
```{r step2a}
#Remove 'old' and 'unbagged' flowers (not sure what 'old' means, and measuring 'old' flowers could be problematic for single-day flowers)
#Also remove measurements from unknown species: UNKN-CAVENDISHIA, UNKN-IMPATIENS, and HETO x HELA
nectar_bagged <- nectar %>%
  filter(!(grepl("Old", flowerAge, fixed = FALSE, ignore.case = FALSE))) %>%
  filter(bagged == "yes") %>%
  mutate_at(c("nectarVol", "nectarConc"), as.numeric) %>%
  filter(!is.na(speciesName))
```

Summarize measurements for nectar concentration
```{r step2b}
concentration_sum <- nectar_bagged %>%
  group_by(species, speciesName, family) %>%
  calculate_basic_summary_stats(variable = nectarConc) %>%
  ungroup() %>%
  select(-n) %>%
  rename(mean_conc = mean, sd_conc = sd, min_conc = min, max_conc = max, median_conc = median)

#Note: If max=33, there were values above the max refractometer reading (32%)
```

Summarize measurements for nectar volume
```{r step2c}
volume_sum <- nectar_bagged %>%
  group_by(species, speciesName, family)%>%
    calculate_basic_summary_stats(variable = nectarVol) %>%
  ungroup() %>%
  select(-n) %>%
  rename(mean_vol = mean, sd_vol = sd, min_vol = min, max_vol = max, median_vol = median)
```

Summarize sample size
```{r step2d}
#SAMPLE SIZE SUMMARY *INCLUDING* FLOWERS WITH ZERO NECTAR
sum_with_zero_volume <- nectar_bagged %>%
  group_by(species, speciesName) %>%
  summarise(numFlowers_inclZero = n()) %>%
  ungroup() %>%
  arrange(desc(numFlowers_inclZero))

#SAMPLE SIZE SUMMARY *EXCLUDING* FLOWERS WITH ZERO NECTAR
sum_without_zero_volume <- nectar_bagged %>%
  filter(nectarVol > 0.00) %>% #Only including nectar amounts >0
  group_by(species, speciesName) %>%
  summarise(numFlowers_notZero=n()) %>%
  ungroup() %>%
  arrange(desc(numFlowers_notZero))

#SAMPLE SIZE SUMMARY *EXCLUDING* FLOWERS WITH NO BRIX MEASUREMENTS
sum_without_missing_conc <- nectar_bagged %>%
  filter(!is.na(nectarConc)) %>% #Only including flowers with measured concentrations
  group_by(species, speciesName) %>%
  summarise(numFlowers_withBrix=n()) %>%
  ungroup() %>%
  arrange(desc(numFlowers_withBrix))

#COMBINING ALL OF THE SAMPLE SIZE SUMMARIES FROM ABOVE
sample_size_sum <- sum_with_zero_volume %>%
  left_join(sum_without_zero_volume) %>%
  left_join(sum_without_missing_conc) %>%
  mutate_at(vars(numFlowers_withBrix), list(~ifelse(is.na(.), 0, .))) #Replace zeroes with NA
```

Combine nectar/conc summary with sample size summary
```{r step2e}
nectar_sum <- volume_sum %>%
  left_join(concentration_sum) %>%
  left_join(sample_size_sum) %>%
  select(species, speciesName, family, everything()) %>%
  mutate_if(is.numeric, ~round(., digits=2)) %>%
  arrange(family)
```

## Step 3: Compile some info for supplemental methods

```{r step3}
#How many species measured?
species_sampled <- nectar_bagged %>%
  distinct(speciesName) %>%
  filter(!is.na(speciesName)) %>%
  pull(speciesName) %>%
  length()

species_sampled

#How many flowers sampled?
flowers_sampled <- nectar_bagged %>%
  pull(speciesName) %>%
  length()
  
flowers_sampled

#How many flowers measured in 2014 vs. 2018?

flowers_per_dataset <- nectar_bagged %>%
  group_by(dataset) %>%
  summarise(num_flowers = n()) %>%
  ungroup()

flowers_per_dataset

#What time of day were flowers collected, on average? Or median
collection_time_sum <- nectar_bagged %>%
  mutate(timeCollected = lubridate::hm(timeCollected)) %>% #This creates a period object
  mutate(timeCollected = lubridate::period_to_seconds(timeCollected)) %>% ##Convert period object to seconds to do math
  calculate_basic_summary_stats(variable = timeCollected) %>%
  mutate_at(vars(median, mean, sd, min, max), lubridate::seconds_to_period) ##Convert back to period object

collection_time_sum

#How many plants were measured with OSU refractometer (not temperature calibrated) vs Rice refractometer (temperature calibrated)?
flowers_per_refractometer <- nectar_bagged %>%
  group_by(refractometerID) %>%
  summarise(num_flowers = n()) %>%
  ungroup()

flowers_per_refractometer

#Percentage of flowers from non-temp calibrated refractometer
(flowers_per_refractometer %>% filter(refractometerID == "OSU") %>% pull(num_flowers))/flowers_sampled

#How many plants and species had nectar concentrations above the max of the refractometer? These have nectar concentrations of 33 degrees Brix.
flowers_above_limit <- nectar_bagged %>%
  filter(nectarConc == 33) %>% 
  group_by(species, speciesName) %>%
  summarise(num_flowers = n()) %>%
  ungroup()

(flowers_above_limit %>% summarise(num_flowers = sum(num_flowers)) %>% pull(num_flowers)/flowers_sampled)
```

## Step 4: Export data
```{r step4}
write.csv(nectar_sum, "../../data/export/supp_tables/Nectar_volume_and_concentration_summary.csv")
```